### 2017-12-01 Task Schedule/Task Schedule.tex
Convert 'Task Schedule' document to a Latex file

\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{chngcntr}
\usepackage{enumitem}
\usepackage[small]{titlesec}
\newlist{paragraphlist}{enumerate}{1}

\setlist[paragraphlist,1]{leftmargin=*,label={\bfseries \arabic*}}

\counterwithin{paragraphlisti}{subsubsection}

\title{{\Huge   Task Schedule}}

\author{Stav Alfi and Shachar Rosenman}

\date{\today}

\begin{document}
\maketitle

\begin{Large}
Feature 1: Getting started. \colorbox{gray!10}{IN PROGRESS}
\end{Large}

\begin{enumerate}[label=(\roman*)]

\item Understand what .torrent files are.
\item How to communicate with a tracker.
\item How to communicate with a peer.
\item Paper - Introduction and related work.
\end{enumerate}

\section{PBI-1: Create work space. DONE}
\begin{enumerate}
\item Git repository – GitHub. \colorbox{gray!20}{DONE}
\item Configure branch protection + pull request.  \colorbox{gray!20}{DONE}
\item Create automatic build: compilation + Units tests + cucumber tests – Travis-CI.  \colorbox{gray!20}{DONE}
\end{enumerate}

\section{PBI-2: Shachar training. IN PROGRESS}
\begin{enumerate}
\item Git - add,commit,branch,checkout,merge,push,fetch.  \colorbox{gray!20}{IN PROGRESS} (shachar)
\item Github - pull requests. \colorbox{gray!20}{IN PROGRESS} (shachar)
\item Travis-CI - understand what it is and how to run a build. \colorbox{gray!20}{IN PROGRESS} (shachar)
\item Cucucmber - feature,scenario,steps,step-definition,debug steps. \colorbox{gray!20}{IN PROGRESS} (shachar)
\end{enumerate}

\section{PBI-3: Fully understand torrent file structure. DONE}
\begin{enumerate}
\item List of information types which are saved in a .torrent file. \colorbox{gray!20}{DONE} (shachar, stav)
\item Understand how much parts there are for a file. Where can we get this information for each torrent \item file. \colorbox{gray!20}{DONE} (shachar, stav)
\item What library in java we need to use to read and analyze .torrent files. \colorbox{gray!20}{DONE} (shachar, stav)
\end{enumerate}

\section{PBI-4: Get details about a given tracker. DONE}
\begin{enumerate}
\item Find the protocol and port which enable us to communicate with a given tracker. \colorbox{gray!20}{DONE} (stav)
\item List the methods we can run on a given tracker. \colorbox{gray!20}{DONE} (stav)
\item Get list of peers information from this tracker on a specific torrent. \colorbox{gray!20}{DONE} (stav)
\item Extract a peers IP from a seeder information. \colorbox{gray!20}{DONE} (stav)
\end{enumerate}

\section{PBI-5: Communicate with a seeder. IN PROGRESS}
\begin{enumerate}
\item Find the protocol and port which enable us to communicate with a seeder. \colorbox{gray!20}{IN PROGRESS} (stav)
\item List the methods we can run on a given seeder. \colorbox{gray!20}{NOT STARTED}
\item Ask if he have the file specified by the torrent file. \colorbox{gray!20}{NOT STARTED}
\item Which parts a seeder have from a file until now. \colorbox{gray!20}{NOT STARTED}
\item Download one random part from a seeder. \colorbox{gray!20}{NOT STARTED}
\end{enumerate}

\section{PBI-6: Others. NOT STARTED}
\begin{enumerate}
\item Learn how to work with latex.
\item transform this file to latex.
\item Create a paper on: \colorbox{gray!20}{NOT STARTED} 14.12.17
\begin{enumerate}
\item What are we building.
\item How client torrent application work.
\item What our application do,add,won't do compared to other client torrent applications.
\item How our application will work including technologies.
\end{enumerate}
\end{enumerate}

\end{document}

### 2017-12-10 paper/paper.tex
created paper file in latex

\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{chngcntr}
\usepackage{enumitem}
\usepackage[small]{titlesec}
\newlist{paragraphlist}{enumerate}{1}

\setlist[paragraphlist,1]{leftmargin=*,label={\bfseries \arabic*}}

\counterwithin{paragraphlisti}{subsubsection}

\title{{\Huge   Introduction and Related work}}

\author{Stav Alfi and Shachar Rosenman}

\date{\today}

\begin{document}
\maketitle

\section*{What are we building.}
In recent years, BitTorrent has emerged as a very scalable peer-to-peer file distribution mechanism.
Because of the great popularity of the BitTorrent there is a lot of interest among the scientific community on whether it is possible to improve the performance of this protocol.
  So many measurement and analytical studies have published suggestions for different algorithms that achieves performance improvements.

Our goal is to select an algorithm, study it and then implement it to prove that the theoretical assumptions are indeed proven in experiments. Then we can publish it so users can enjoy even better performance

study
Our goal is to select an algorithm that is most effective and implement it

\section*{How BitTorrent Works.}
BitTorrent is a peer-to-peer protocol, which means that the computers in a BitTorrent “swarm” (a group of computers downloading and uploading the same torrent) transfer data between each other without the need for a central server, Where all the information passes through a particular server.
while  The tracker server keeps track of where file copies reside on peer machines, which ones are available at time of the client request, and helps coordinate efficient transmission and reassembly of the copied file.

Traditionally, a computer joins a BitTorrent swarm by loading a torrent file into a BitTorrent client. The BitTorrent client contacts a “tracker” specified in the .torrent file. The tracker is a special server that keeps track of the connected computers. The tracker shares IP addresses with other BitTorrent clients in the swarm, allowing clients to connect to each other.

Once connected, a BitTorrent client downloads pieces of the files ,Each file to be distributed is divided into small information chunks called pieces. Downloading peers achieve rapid download speeds by requesting multiple pieces from different computers simultaneously in the swarm.
The torrent
application download each peace and combine them togheter. Once the BitTorrent client has some data, it can then begin to upload that data to other BitTorrent clients in the swarm. There are three types involved in the distribution process:

\textbf{Seeder}  is a person who has a torrent file open in their client and they have the complete file downloaded already.

\textbf{Leechers} are those who are downloading and uploading at the same time. If a user starts sharing a file that he already has, and downloads what other users have already uploaded or are in the process of uploading a torrent file, he becomes a leecher.

\textbf{peers}  is someone who is both downloading and uploading the file in the swarm. Files are downloaded in pieces. When a user downloads some pieces, he then automatically starts uploading it.A file will be downloaded faster if more people are involved in the swarm. A peer becomes a seed when he has completed 100% of the file and wishes to continue uploading.

\textbf{Public IP} address is the address that is assigned to a computing device to allow direct access over the Internet. A web server, email server and any server device directly accessible from the Internet are candidate for a public IP address. A public IP address is globally unique, and can only be assigned to a unique device.
Private ip

\textbf{private IP} address is the address space allows to create local network. When a computer is assigned a private IP address, the local devices see this computer via it's private IP address. However, the devices residing outside of the local network cannot directly communicate via the private IP address, but uses your router's public IP address to communicate. To allow direct access to a local device which is assigned a private IP address, a Network Address Translator (NAT) should be used.

\textbf{NAT} is a method of remapping one IP address space into another, the majority of NATs map multiple private hosts to one publicly exposed IP address. In a typical configuration, a local network uses one of the designated private IP address. 
A router on that network has a private address in that address space. The router is also connected to the Internet with a public address. As traffic passes from the local network to the Internet, the source address in each packet is translated on the fly from a private address to the public address. The router tracks basic data about each active connection (particularly the destination address and port). When a reply returns to the router, it uses the connection tracking data it stored during the outbound phase to determine the private address on the internal network to which to forward the reply

the system works fine until you want to give people on the outside Internet
access to files. when they try to reach the computer through the public IP address they actually reach the router and the router doesn't know how to forward the connection to the appropriate computer, this way a leecher can not find the computer that has the file
unless it's been told how to do so.

telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.

To save the trouble of keeping track of ports and configuring routers many NAT routers now have what is called \textbf{universal plug in play (UPnP)} . when UPNP is enabled on the router applications on the computer can manage the forwarding themselves, the program will tell the router which port it will be receiving requests on, and the router will set up the necessary forwarding, so that information from the outside Internet can be directed to the appropriate local computer. this allows the ports to be managed by server based programs from the computers they belong to making network management less of a hassle. there are times though when you PNP either isn't available on the router or isn't enabled for security purposes and manual port forwarding becomes necessary.

\end{document}

### 2017-12-10 paper/paper.tex
updated the paper file and removed the task-schedule file with latex version

@@
 
-\section*{What are we building.}
-In recent years, BitTorrent has emerged as a very scalable peer-to-peer file distribution mechanism.
+  \section*{Introduction}
+  \begin{flushleft}
+
+    TorrentX is a client side software for downloading and uploading torrents through the internet.
+    There is a support for downloading and uploading the same torrent through a cluster which located in your private network.
+This architecture let us discover and use more seeders by examining more of them on different virtual/physical machines on a cluster.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    TorrentX core algorithms will be developed by us from scratch.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    In the recent years, BitTorrent has emerged as a scalable peer-to-peer file distribution mechanism.
     Because of the great popularity of the BitTorrent there is a lot of interest among the scientific community on whether it is possible to improve the performance of this protocol.
@@
 
+  \end{flushleft}
+  \begin{flushleft}
+
     Our goal is to select an algorithm, study it and then implement it to prove that the theoretical assumptions are indeed proven in experiments.
 Then we can publish it so users can enjoy even better performance
+  \end{flushleft}
 
-study
-Our goal is to select an algorithm that is most effective and implement it
+  \section*{How BitTorrent Works}
+  \begin{flushleft}
 
-\section*{How BitTorrent Works.}
-BitTorrent is a peer-to-peer protocol, which means that the computers in a BitTorrent “swarm” (a group of computers downloading and uploading the same torrent) transfer data between each other without the need for a central server, Where all the information passes through a particular server.
-while  The tracker server keeps track of where file copies reside on peer machines, which ones are available at time of the client request, and helps coordinate efficient transmission and reassembly of the copied file.
+    BitTorrent is a peer-to-peer protocol, which means that the computers in a BitTorrent “swarm” (a group of computers downloading and uploading the same torrent) transfer data between each other without the need for a central server, where all the information passes through a particular server.
+    while the tracker server keeps track of where file copies reside on peer machines, which ones are available at time of the client request, and helps coordinate efficient transmission and reassembly of the copied file.
 
-Traditionally, a computer joins a BitTorrent swarm by loading a torrent file into a BitTorrent client.
-The BitTorrent client contacts a “tracker” specified in the .torrent file.
-The tracker is a special server that keeps track of the connected computers.
-The tracker shares IP addresses with other BitTorrent clients in the swarm, allowing clients to connect to each other.
+  \end{flushleft}
+  \begin{flushleft}
 
-Once connected, a BitTorrent client downloads pieces of the files ,Each file to be distributed is divided into small information chunks called pieces.
-Downloading peers achieve rapid download speeds by requesting multiple pieces from different computers simultaneously in the swarm.
-The torrent
-application download each peace and combine them togheter.
-Once the BitTorrent client has some data, it can then begin to upload that data to other BitTorrent clients in the swarm.
-There are three types involved in the distribution process:
+    A server who responsible for saving the leechers (threads which attempting to download a torrent) and seeders (leechers who finished downloading the torrent) information is called a tracker.
+When a new leecher want to download, it sends a request to one of the avilable trackers in the torrent file and ask for all the peers (leechers and seeders).
+This request is called announcement.
 
-\textbf{Seeder}  is a person who has a torrent file open in their client and they have the complete file downloaded already.
+  \end{flushleft}
+  \begin{flushleft}
 
-\textbf{Leechers} are those who are downloading and uploading at the same time.
-If a user starts sharing a file that he already has, and downloads what other users have already uploaded or are in the process of uploading a torrent file, he becomes a leecher.
+    It is importent to note that the tracker is refering to every peer by peer-public-ip.
 
-\textbf{peers}  is someone who is both downloading and uploading the file in the swarm.
-Files are downloaded in pieces.
-When a user downloads some pieces, he then automatically starts uploading it.A file will be downloaded faster if more people are involved in the swarm.
-A peer becomes a seed when he has completed 100% of the file and wishes to continue uploading.
+  \end{flushleft}
+  \begin{flushleft}
 
@@
 A public IP address is globally unique, and can only be assigned to a unique device.
-Private ip
 
-\textbf{private IP} address is the address space allows to create local network.
-When a computer is assigned a private IP address, the local devices see this computer via it's private IP address.
-However, the devices residing outside of the local network cannot directly communicate via the private IP address, but uses your router's public IP address to communicate.
-To allow direct access to a local device which is assigned a private IP address, a Network Address Translator (NAT) should be used.
+  \end{flushleft}
+  \begin{flushleft}
 
-\textbf{NAT} is a method of remapping one IP address space into another, the majority of NATs map multiple private hosts to one publicly exposed IP address.
+    Once a leecher is getting response from the tracker about a request to specific torrent's peer list, the leecher's BitTorrent client software downloads the pieces of the files.
+Each file in the torrent is divided into small information chunks called pieces.
+Each peace in the torrent have a constant size except the last peace.
+A peace size is defined in the torrent file.
+All in all, We can conclude that peers exchange peaces of multiple torrents concurrently in a distributed system.
+
+  \end{flushleft}
+
+  \section*{Peers massages}
+  \begin{flushleft}
+
+    To better understand how a given torrent algorithm works, we must understand what types of messages are transfered between peers in the p2p (peer-to-peer) protocol.
+Every message is described in the p2p protocol by what it's size must be, what it's content and by what order.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    1.
+The keep-alive message is a message with zero bytes, specified with the length prefix set to zero.
+There is no message ID and no payload (extra data).
+Peers may close a connection if they receive no messages (keep-alive or any other message) for a certain period of time, so a keep-alive message must be sent to maintain the connection alive if no command have been sent for a given amount of time.
+This amount of time is generally two minutes.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    2.
+Choke message means that if peer1 send it to peer2, then peer1 will ignore any future requests for peaces.
+We can conclude that peer1 is too busy.
+The choke message is fixed-length and has no payload.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    3. Unchoke message means that if peer1 send it to peer2, then peer1 will no longer ignore any future requests for peaces. The unchoke message is fixed-length and has no payload.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    4. Interested message means that if peer1 send it to peer2, peer1 want peaces which peer2 have to offer. The interested message is fixed-length and has no payload.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    5. Not interested message means that if peer1 send it to peer2, peer1 does not want any peaces which peer2 have to offer.The not interested message is fixed-length and has no payload.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    6. The have message is fixed length. The payload is the zero-based index of a piece that has just been successfully downloaded and verified via the hash.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    Implementer's Note: That is the strict definition, in reality some games may be played.
+In particular because peers are extremely unlikely to download pieces that they already have, a peer may choose not to advertise having a piece to a peer that already has that piece.
+At a minimum "HAVE suppression" will result in a 0.5 reduction in the number of HAVE messages, this translates to around a 25-35% reduction in protocol overhead.
+At the same time, it may be worthwhile to send a HAVE message to a peer that has that piece already since it will be useful in determining which piece is rare.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    7.
+The bitfield message may only be sent immediately after the handshaking sequence is completed, and before any other messages are sent.
+It is optional, and need not be sent if a client has no pieces.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    The bitfield message is variable length, where X is the length of the bitfield.
+The payload is a bitfield representing the pieces that have been successfully downloaded.
+The high bit in the first byte corresponds to piece index 0.
+Bits that are cleared indicated a missing piece, and set bits indicate a valid and available piece.
+Spare bits at the end are set to zero.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    A bitfield of the wrong length is considered an error.
+Clients should drop the connection if they receive bitfields that are not of the correct size, or if the bitfield has any of the spare bits set.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    8.
+The request message is fixed length, and is used to request a block.
+The payload contains the following information: Index: integer specifying the zero-based piece index.
+Begin: integer specifying the zero-based byte offset within the piece.
+Length: integer specifying the requested length.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    9.
+he piece message is variable length, where X is the length of the block.
+The payload contains the following information: Index: integer specifying the zero-based piece index.
+Begin: integer specifying the zero-based byte offset within the piece.
+Block: block of data, which is a subset of the piece specified by index.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    10.
+The cancel message is fixed length, and is used to cancel block requests.
+The payload is identical to that of the "request" message.
+It is typically used during "End Game" (see the Algorithms section below).
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    Downloading peers achieve rapid download speeds by requesting multiple pieces from different computers simultaneously in the swarm.
+    The torrent application download each peace and combine them togheter. Once the BitTorrent client has some data, it can then begin to upload that data to other BitTorrent clients in the swarm.
+
+  \end{flushleft}
+  \begin{flushleft}
+  \end{flushleft}
+  \begin{flushleft}
+
+    Because multiple machines listen to the same port in the same network, we need to be able to get response from the WAN to the LAN.
+In short, \textbf{NAT} is a method of remapping public IP address and a port number to private ip address and a port number and vice versa.
+The majority of NATs map multiple private hosts to one publicly exposed IP address.
 In a typical configuration, a local network uses one of the designated private IP address.
@@
 The router tracks basic data about each active connection (particularly the destination address and port).
-When a reply returns to the router, it uses the connection tracking data it stored during the outbound phase to determine the private address on the internal network to which to forward the reply
+When a reply returns to the router, it uses the connection tracking data it stored during the outbound phase to determine the private address on the internal network to which to forward the reply the system works fine until you want to give people on the outside Internet access to files.
+When they try to reach the computer through the public IP address they actually reach the router and the router doesn't know how to forward the connection to the appropriate computer, this way a leecher can not find the computer that has the file unless it's been told how to do so.
 
-the system works fine until you want to give people on the outside Internet
-access to files.
-when they try to reach the computer through the public IP address they actually reach the router and the router doesn't know how to forward the connection to the appropriate computer, this way a leecher can not find the computer that has the file
-unless it's been told how to do so.
+    A Bittorrent client application listen to a specific port in every machine.
+To be able to add this port to the NAT in it's router, one must use \textbf{universal plug in play (UPnP)} to avoid menually adding a port and a ip address to the NAT.
+The UPNP is a way to configure the NAT in any programming language.
+Telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.
 
-telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.
+  \end{flushleft}
 
-To save the trouble of keeping track of ports and configuring routers many NAT routers now have what is called \textbf{universal plug in play (UPnP)} .
-when UPNP is enabled on the router applications on the computer can manage the forwarding themselves, the program will tell the router which port it will be receiving requests on, and the router will set up the necessary forwarding, so that information from the outside Internet can be directed to the appropriate local computer.
-this allows the ports to be managed by server based programs from the computers they belong to making network management less of a hassle.
-there are times though when you PNP either isn't available on the router or isn't enabled for security purposes and manual port forwarding becomes necessary.
+  \section*{Algorithms}
+  \begin{flushleft}
+    \textbf{Super Seeding} is a new seeding algorithm designed to help a torrent initiator with limited bandwidth "pump up" a large torrent, reducing the amount of data it needs to upload in order to spawn new seeds in the torrent.
 
+  \end{flushleft}
+  \begin{flushleft}
+
+    When a seeding client enters "super-seed mode", it will not act as a standard seed, but masquerades as a normal client with no data.
+As clients connect, it will then inform them that it received a piece -- a piece that was never sent, or if all pieces were already sent, is very rare.
+This will induce the client to attempt to download only that piece.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    When the client has finished downloading the piece, the seed will not inform it of any other pieces until it has seen the piece it had sent previously present on at least one other client.
+Until then, the client will not have access to any of the other pieces of the seed, and therefore will not waste the seed's bandwidth.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    This method has resulted in much higher seeding efficiencies, by both inducing peers into taking only the rarest data, reducing the amount of redundant data sent, and limiting the amount of data sent to peers which do not contribute to the swarm.
+Prior to this, a seed might have to upload 150% to 200% of the total size of a torrent before other clients became seeds.
+However, a large torrent seeded with a single client running in super-seed mode was able to do so after only uploading 105% of the data.
+This is 150-200% more efficient than when using a standard seed.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    Super-seed mode is 'NOT recommended for general use.
+While it does assist in the wider distribution of rare data, because it limits the selection of pieces a client can downlad, it also limits the ability of those clients to download data for pieces they have already partially retrieved.
+Therefore, super-seed mode is only recommended for initial seeding servers.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    \textbf{End game algorithm} - When a download is almost complete, there's a tendency for the last few blocks to trickle in slowly.
+To speed this up, the client sends requests for all of its missing blocks to all of its peers.
+To keep this from becoming horribly inefficient, the client also sends a cancel to everyone else every time a block arrives.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    There is no documented thresholds, recommended percentages, or block counts that could be used as a guide or Recommended Best Practice here.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    When to enter end game mode is an area of discussion.
+Some clients enter end game when all pieces have been requested.
+Others wait until the number of blocks left is lower than the number of blocks in transit, and no more than 20.
+There seems to be agreement that it's a good idea to keep the number of pending blocks low (1 or 2 blocks) to minimize the overhead, and if you randomize the blocks requested, there's a lower chance of downloading duplicates.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    \textbf{Choking and optimistic Unchoking algorithm} - Choking is done for several reasons.
+TCP congestion control behaves very poorly when sending over many connections at once.
+Also, choking lets each peer use a tit-for-tat-ish algorithm to ensure that they get a consistent download rate.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    The choking algorithm described below is the currently deployed one.
+It is very important that all new algorithms work well both in a network consisting entirely of themselves and in a network consisting mostly of this one.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    There are several criteria a good choking algorithm should meet.
+It should cap the number of simultaneous uploads for good TCP performance.
+It should avoid choking and unchoking quickly, known as 'fibrillation'.
+It should reciprocate to peers who let it download.
+Finally, it should try out unused connections once in a while to find out if they might be better than the currently used ones, known as optimistic unchoking.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    The currently deployed choking algorithm avoids fibrillation by only changing choked peers once every ten seconds.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    Reciprocation and number of uploads capping is managed by unchoking the four peers which have the best upload rate and are interested.
+This maximizes the client's download rate.
+These four peers are referred to as downloaders, because they are interested in downloading from the client.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    Peers which have a better upload rate (as compared to the downloaders) but aren't interested get unchoked.
+If they become interested, the downloader with the worst upload rate gets choked.
+If a client has a complete file, it uses its upload rate rather than its download rate to decide which peers to unchoke.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    For optimistic unchoking, at any one time there is a single peer which is unchoked regardless of its upload rate (if interested, it counts as one of the four allowed downloaders).
+Which peer is optimistically unchoked rotates every 30 seconds.
+Newly connected peers are three times as likely to start as the current optimistic unchoke as anywhere else in the rotation.
+This gives them a decent chance of getting a complete piece to upload.
+
+  \end{flushleft}
+  \begin{flushleft}
+
+    \textbf{Anti-snubbing} - Occasionally a BitTorrent peer will be choked by all peers which it was formerly downloading from.
+In such cases it will usually continue to get poor download rates until the optimistic unchoke finds better peers.
+To mitigate this problem, when over a minute goes by without getting any piece data while downloading from a peer, BitTorrent assumes it is "snubbed" by that peer and doesn't upload to it except as an optimistic unchoke.
+This frequently results in more than one concurrent optimistic unchoke, (an exception to the exactly one optimistic unchoke rule mentioned above), which causes download rates to recover much more quickly when they falter.
+
+  \end{flushleft}
+
+  \section*{Our application}
+  \begin{flushleft}
+
+    In short, a leecher can choose to download the peaces in a specific order (from the first peace to the last) so one can watch a movie while downloading it.
+
+  \end{flushleft}
 \end{document}

### 2017-12-13 paper/paper.tex
added advisor to the paper
correcting errors in the first four pages in paper file

@@
 
-\author{Stav Alfi and Shachar Rosenman}
+\author{Stav Alfi, Shachar Rosenman\\{\small Advisor: Prof. Dan Hefetz}}
 
@@
     TorrentX is a client side software for downloading and uploading torrents through the internet.
-    There is a support for downloading and uploading the same torrent through a cluster which located in your private network.
-This architecture let us discover and use more seeders by examining more of them on different virtual/physical machines on a cluster.
+    There is support for downloading and uploading the same torrent through a cluster which is located in your private network.
+This architecture lets  us discover and use more seeders by examining more of them on different virtual/physical machines on a cluster.
 
@@
 
-    In the recent years, BitTorrent has emerged as a scalable peer-to-peer file distribution mechanism.
+    In recent years, BitTorrent has emerged as a scalable peer-to-peer file distribution mechanism.
     Because of the great popularity of the BitTorrent there is a lot of interest among the scientific community on whether it is possible to improve the performance of this protocol.
-    So many measurement and analytical studies have published suggestions for different algorithms that achieves performance improvements.
+    So many measurement and analytical studies have published suggestions for different algorithms that achieve performance improvements.
 
@@
     BitTorrent is a peer-to-peer protocol, which means that the computers in a BitTorrent “swarm” (a group of computers downloading and uploading the same torrent) transfer data between each other without the need for a central server, where all the information passes through a particular server.
-    while the tracker server keeps track of where file copies reside on peer machines, which ones are available at time of the client request, and helps coordinate efficient transmission and reassembly of the copied file.
+    The tracker server keeps track of where file copies reside on peer machines, which ones are available at the time of the clients request, and helps coordinate efficient transmission and reassembly of the copied file.
 
@@
 
-    A server who responsible for saving the leechers (threads which attempting to download a torrent) and seeders (leechers who finished downloading the torrent) information is called a tracker.
-When a new leecher want to download, it sends a request to one of the avilable trackers in the torrent file and ask for all the peers (leechers and seeders).
+    A server who is responsible for saving the leechers (threads which  are attempting to download a torrent) and seeders (leechers who finished downloading the torrent) information is called a tracker.
+When a new leecher wants to download, it sends a request to one of the available trackers in the torrent file and asks for all the peers (leechers and seeders).
 This request is called announcement.
@@
 
-    It is importent to note that the tracker is refering to every peer by peer-public-ip.
+    It is important to note that the tracker is referring to every peer by peer-public-ip.
 
@@
 
-    Once a leecher is getting response from the tracker about a request to specific torrent's peer list, the leecher's BitTorrent client software downloads the pieces of the files.
+    Once a leecher is getting a response from the tracker about a request to a specific torrent's peer list, the leecher's BitTorrent client software downloads the pieces of the files.
 Each file in the torrent is divided into small information chunks called pieces.
-Each peace in the torrent have a constant size except the last peace.
-A peace size is defined in the torrent file.
-All in all, We can conclude that peers exchange peaces of multiple torrents concurrently in a distributed system.
+Each piece in the torrent has a same size except the last piece.
+A piece size is defined in the torrent file.
+All in all, We can conclude that peers exchange piece of multiple torrents concurrently in a distributed system.
 
@@
 
-  \section*{Peers massages}
+  \section*{Peers messages}
   \begin{flushleft}
@@
     To better understand how a given torrent algorithm works, we must understand what types of messages are transfered between peers in the p2p (peer-to-peer) protocol.
-Every message is described in the p2p protocol by what it's size must be, what it's content and by what order.
+Every message is described in the p2p protocol by what its size must be, what its content and by what order.
 
@@
 There is no message ID and no payload (extra data).
-Peers may close a connection if they receive no messages (keep-alive or any other message) for a certain period of time, so a keep-alive message must be sent to maintain the connection alive if no command have been sent for a given amount of time.
+Peers may close a connection if they receive no messages (keep-alive or any other message) for a certain period of time, so a keep-alive message must be sent to maintain the connection alive if no command has been sent for a given amount of time.
 This amount of time is generally two minutes.
@@
 
-    2.
-Choke message means that if peer1 send it to peer2, then peer1 will ignore any future requests for peaces.
-We can conclude that peer1 is too busy.
-The choke message is fixed-length and has no payload.
+    2. Choke message means that if peer(i) sends it to peer(j), then peer(i) will ignore any future requests for pieces. The choke message is fixed-length and has no payload.
 
@@
 
-    3. Unchoke message means that if peer1 send it to peer2, then peer1 will no longer ignore any future requests for peaces. The unchoke message is fixed-length and has no payload.
+    3. Unchoke message means that if peer(i) sends it to peer(j), then peer(i) will no longer ignore any future requests for pieces. The unchoke message is fixed-length and has no payload.
 
@@
 
-    4. Interested message means that if peer1 send it to peer2, peer1 want peaces which peer2 have to offer. The interested message is fixed-length and has no payload.
+    4. Interested message means that if peer(i) sends it to peer(j), peer(i) wants peaces which peer(j) has to offer.  The interested message is fixed-length and has no payload.
 
@@
 
-    5. Not interested message means that if peer1 send it to peer2, peer1 does not want any peaces which peer2 have to offer.The not interested message is fixed-length and has no payload.
+    5. Not interested message means that if peer(i) send it to peer(j), peer(i) does not want any peaces which peer(j) have to offer.The not interested message is fixed-length and has no payload.
 
@@
     6. The have message is fixed length. The payload is the zero-based index of a piece that has just been successfully downloaded and verified via the hash.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    Implementer's Note: That is the strict definition, in reality some games may be played.
-In particular because peers are extremely unlikely to download pieces that they already have, a peer may choose not to advertise having a piece to a peer that already has that piece.
-At a minimum "HAVE suppression" will result in a 0.5 reduction in the number of HAVE messages, this translates to around a 25-35% reduction in protocol overhead.
-At the same time, it may be worthwhile to send a HAVE message to a peer that has that piece already since it will be useful in determining which piece is rare.
 
@@
 
-    The bitfield message is variable length, where X is the length of the bitfield.
-The payload is a bitfield representing the pieces that have been successfully downloaded.
+    The bitfield message is variable length, /The payload is a bitfield representing the pieces that have been successfully downloaded.
 The high bit in the first byte corresponds to piece index 0.
@@
     9.
-he piece message is variable length, where X is the length of the block.
+The piece message is variable length, where X is the length of the block.
 The payload contains the following information: Index: integer specifying the zero-based piece index.
@@
     Downloading peers achieve rapid download speeds by requesting multiple pieces from different computers simultaneously in the swarm.
-    The torrent application download each peace and combine them togheter. Once the BitTorrent client has some data, it can then begin to upload that data to other BitTorrent clients in the swarm.
+    The torrent application downloads each piece and combines them together. Once the BitTorrent client has some data, it can then begin to upload that data to other BitTorrent clients in the swarm.
 
@@
 
-    Because multiple machines listen to the same port in the same network, we need to be able to get response from the WAN to the LAN.
-In short, \textbf{NAT} is a method of remapping public IP address and a port number to private ip address and a port number and vice versa.
+    Because multiple machines listen to the same port in the same network, we need to be able to get a response from the WAN to the LAN.
+In short, \textbf{NAT} is a method of remapping a public IP address and a port number to a private ip address and a port number and vice versa.
 The majority of NATs map multiple private hosts to one publicly exposed IP address.
-In a typical configuration, a local network uses one of the designated private IP address.
+In a typical configuration, a local network uses one of the designated private IP addresses.
 A router on that network has a private address in that address space.
@@
 The router tracks basic data about each active connection (particularly the destination address and port).
-When a reply returns to the router, it uses the connection tracking data it stored during the outbound phase to determine the private address on the internal network to which to forward the reply the system works fine until you want to give people on the outside Internet access to files.
+When a reply returns to the router, it uses the connection tracking data it stored during The outbound phase to determine the private address on the internal network to which to forward the reply.
+the system works fine until you want to give people on the outside Internet access to files.
 When they try to reach the computer through the public IP address they actually reach the router and the router doesn't know how to forward the connection to the appropriate computer, this way a leecher can not find the computer that has the file unless it's been told how to do so.
 
-    A Bittorrent client application listen to a specific port in every machine.
-To be able to add this port to the NAT in it's router, one must use \textbf{universal plug in play (UPnP)} to avoid menually adding a port and a ip address to the NAT.
+    A Bittorrent client application listens to a specific port in every machine.
+To be able to add this port to the NAT in its router, one must use \textbf{universal plug in play (UPnP)} to avoid manually adding a port and a ip address to the NAT.
 The UPNP is a way to configure the NAT in any programming language.

### 2017-12-13 paper/paper.tex
fixed paper

--- 2017-12-10 paper/paper.tex
@@
 \documentclass[11pt]{article}
-
+\usepackage{hyperref}
 \usepackage{xcolor}
@@
     A Bittorrent client application listen to a specific port in every machine.
-To be able to add this port to the NAT in it's router, one must use \textbf{universal plug in play (UPnP)} to avoid menually adding a port and a ip address to the NAT.
+To be able to add this port to the NAT in it's router, one must use \textbf{universal plug in play (UPnP)} to avoid menually adding a port and a IP address to the NAT.
 The UPNP is a way to configure the NAT in any programming language.
@@
   \begin{flushleft}
-    \textbf{Super Seeding} is a new seeding algorithm designed to help a torrent initiator with limited bandwidth "pump up" a large torrent, reducing the amount of data it needs to upload in order to spawn new seeds in the torrent.
+    \textbf{Super Seeding} is a new seeding algorithm designed to help a torrent initiator (The first seeder) with limited bandwidth to "pump up" a large torrent, reducing the amount of data it needs to upload in order to spawn new seeds in the torrent.
 
@@
 
-    When a seeding client enters "super-seed mode", it will not act as a standard seed, but masquerades as a normal client with no data.
+    When a seeding client enters "super-seed mode", it does not act as a standard seed, but masquerades as a normal client with no data.
 As clients connect, it will then inform them that it received a piece -- a piece that was never sent, or if all pieces were already sent, is very rare.
@@
     This method has resulted in much higher seeding efficiencies, by both inducing peers into taking only the rarest data, reducing the amount of redundant data sent, and limiting the amount of data sent to peers which do not contribute to the swarm.
-Prior to this, a seed might have to upload 150% to 200% of the total size of a torrent before other clients became seeds.
-However, a large torrent seeded with a single client running in super-seed mode was able to do so after only uploading 105% of the data.
-This is 150-200% more efficient than when using a standard seed.
+Prior to this, a seed might have to upload 150\% to 200\% of the total size of a torrent before other clients became seeds.
+However, a large torrent seeded with a single client running in super-seed mode was able to do so after only uploading 105\% of the data.
+This is 150-200\% more efficient than when using a standard seed.
 
@@
     Super-seed mode is 'NOT recommended for general use.
-While it does assist in the wider distribution of rare data, because it limits the selection of pieces a client can downlad, it also limits the ability of those clients to download data for pieces they have already partially retrieved.
+While it does assist in the wider distribution of rare data, because it limits the selection of pieces a client can download, it also limits the ability of those clients to download data for pieces they have already partially retrieved.
 Therefore, super-seed mode is only recommended for initial seeding servers.
@@
 Others wait until the number of blocks left is lower than the number of blocks in transit, and no more than 20.
-There seems to be agreement that it's a good idea to keep the number of pending blocks low (1 or 2 blocks) to minimize the overhead, and if you randomize the blocks requested, there's a lower chance of downloading duplicates.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    \textbf{Choking and optimistic Unchoking algorithm} - Choking is done for several reasons.
-TCP congestion control behaves very poorly when sending over many connections at once.
-Also, choking lets each peer use a tit-for-tat-ish algorithm to ensure that they get a consistent download rate.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    The choking algorithm described below is the currently deployed one.
-It is very important that all new algorithms work well both in a network consisting entirely of themselves and in a network consisting mostly of this one.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    There are several criteria a good choking algorithm should meet.
-It should cap the number of simultaneous uploads for good TCP performance.
-It should avoid choking and unchoking quickly, known as 'fibrillation'.
-It should reciprocate to peers who let it download.
-Finally, it should try out unused connections once in a while to find out if they might be better than the currently used ones, known as optimistic unchoking.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    The currently deployed choking algorithm avoids fibrillation by only changing choked peers once every ten seconds.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    Reciprocation and number of uploads capping is managed by unchoking the four peers which have the best upload rate and are interested.
-This maximizes the client's download rate.
-These four peers are referred to as downloaders, because they are interested in downloading from the client.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    Peers which have a better upload rate (as compared to the downloaders) but aren't interested get unchoked.
-If they become interested, the downloader with the worst upload rate gets choked.
-If a client has a complete file, it uses its upload rate rather than its download rate to decide which peers to unchoke.
-
-  \end{flushleft}
-  \begin{flushleft}
-
-    For optimistic unchoking, at any one time there is a single peer which is unchoked regardless of its upload rate (if interested, it counts as one of the four allowed downloaders).
-Which peer is optimistically unchoked rotates every 30 seconds.
-Newly connected peers are three times as likely to start as the current optimistic unchoke as anywhere else in the rotation.
-This gives them a decent chance of getting a complete piece to upload.
+There seems to be an agreement that it's a good idea to keep the number of pending blocks low (1 or 2 blocks) to minimize the overhead, and if you randomize the blocks requested, there's a lower chance of downloading duplicates.
 
@@
   \end{flushleft}
-
   \section*{Our application}
@@
   \end{flushleft}
+  \section*{Sources}
+  \begin{flushleft}
+    1. \href{http://www.rasterbar.com/products/libtorrent/udp_tracker_protocol.html}{udp tracker protocol}
+
+    2. \href{https://wiki.theory.org/index.php/BitTorrentSpecification}{Bit Torrent Specification}
+  \end{flushleft}
 \end{document}

### 2017-12-13 paper/paper.tex

--- 2017-12-13 paper/paper.tex
@@
     A Bittorrent client application listens to a specific port in every machine.
-To be able to add this port to the NAT in its router, one must use \textbf{universal plug in play (UPnP)} to avoid manually adding a port and a ip address to the NAT.
+To be able to add this port to the NAT in its router, one must use \textbf{universal plug in play (UPnP)} to avoid manually adding a port and a IP address to the NAT.
 The UPNP is a way to configure the NAT in any programming language.

### 2018-03-02 src/main/java/main/downloader/TorrentDownloader.java
for each torrent, we will generate new and random and free tcp-port to listen to new peers. (This is an upgrade because until now we listened to a specific port for all the torrents).

@@ -1,6 +1,5 @@
 package main.downloader;
 
-import main.AppConfig;
 import main.TorrentInfo;
 import main.peer.InitializePeersCommunication;
 import main.peer.PeersCommunicator;
@@ -48,10 +47,10 @@ public abstract class TorrentDownloader implements DownloadControl {
     }
 
     public TorrentDownloader(TorrentInfo torrentInfo, Downloader downloader, TrackerProvider trackerProvider) {
-        this(torrentInfo, downloader, trackerProvider.connectToTrackers(),
-                new PeersProvider(torrentInfo, trackerProvider,
-                        new InitializePeersCommunication(torrentInfo,
-                                AppConfig.getInstance().getTcpPortListeningForPeersMessages())),
+        this(torrentInfo,
+                downloader,
+                trackerProvider.connectToTrackers(),
+                new PeersProvider(torrentInfo, trackerProvider, new InitializePeersCommunication(torrentInfo)),
                 trackerProvider);
     }
 

### 2018-03-02 src/main/java/main/peer/InitializePeersCommunication.java

@@ -24,10 +24,10 @@ public class InitializePeersCommunication {
     private ServerSocket listenToPeerConnection;
     private final Flux<PeersCommunicator> allPeersCommunicatorFlux;
 
-    public InitializePeersCommunication(TorrentInfo torrentInfo, int tcpPort) {
+    public InitializePeersCommunication(TorrentInfo torrentInfo) {
         this.torrentInfo = torrentInfo;
         try {
-            this.listenToPeerConnection = new ServerSocket(tcpPort);
+            this.listenToPeerConnection = new ServerSocket(getFreePortOnLocalMachine());
         } catch (IOException e) {
             // TODO: do something with this shit
             e.printStackTrace();
@@ -49,6 +49,10 @@ public class InitializePeersCommunication {
                 }
         })
                 .subscribeOn(Schedulers.elastic());
+    }
+
+    public int getFreePortOnLocalMachine() {
+        return 9097;
     }
 
     public Mono<PeersCommunicator> connectToPeer(Peer peer) {
@@ -153,5 +157,9 @@ public class InitializePeersCommunication {
 
     public void stopListenForNewPeers() throws IOException {
         this.listenToPeerConnection.close();
+    }
+
+    public int getTcpPort() {
+        return this.listenToPeerConnection.getLocalPort();
     }
 }

### 2018-03-02 src/main/java/main/peer/PeersProvider.java

@@ -27,7 +27,11 @@ public class PeersProvider {
     }
 
     public Flux<Peer> getPeers(TrackerConnection trackerConnection) {
-        return trackerConnection.announce(this.torrentInfo.getTorrentInfoHash())
+        return trackerConnection.announce(this.torrentInfo.getTorrentInfoHash(),
+                // unimportant note: this method will not cause the application to listen for new peers on this torrent so
+                // the tcpPort we choose here is useless... we only need this for constructing new
+                // InitializePeersCommunication instance.
+                this.initializePeersCommunication.getTcpPort())
                 .flux()
                 .flatMap(AnnounceResponse::getPeers);
     }
@@ -47,7 +51,7 @@ public class PeersProvider {
     }
 
     public Flux<PeersCommunicator> connectToPeers(TrackerConnection trackerConnection) {
-        return trackerConnection.announce(torrentInfo.getTorrentInfoHash())
+        return trackerConnection.announce(torrentInfo.getTorrentInfoHash(), this.initializePeersCommunication.getTcpPort())
                 .flux()
                 .flatMap(AnnounceResponse::getPeers)
                 .distinct()

### 2018-03-02 src/main/java/main/tracker/TrackerConnection.java

@@ -8,12 +8,10 @@ import main.tracker.response.AnnounceResponse;
 import main.tracker.response.ConnectResponse;
 import main.tracker.response.ScrapeResponse;
 import reactor.core.publisher.Mono;
-import reactor.core.publisher.SignalType;
 
 import java.nio.ByteBuffer;
 import java.util.List;
 import java.util.function.Function;
-import java.util.logging.Level;
 import java.util.stream.Collectors;
 
 public class TrackerConnection extends Tracker {
@@ -25,15 +23,14 @@ public class TrackerConnection extends Tracker {
         this.connectResponse = connectResponse;
     }
 
-    public Mono<? extends AnnounceResponse> announce(String torrentHash) {
+    public Mono<? extends AnnounceResponse> announce(String torrentHash, int tcpPort) {
 
         byte[] peerId = AppConfig.getInstance().getPeerId().getBytes();
-        int portWeListenForPeersRequests = AppConfig.getInstance().getTcpPortListeningForPeersMessages();
         int howMuchPeersWeWant = 1000;
 
         AnnounceRequest announceRequest =
                 new AnnounceRequest(this, this.connectResponse.getConnectionId(),
-                        HexByteConverter.hexToByte(torrentHash), peerId, howMuchPeersWeWant, (short) portWeListenForPeersRequests);
+                        HexByteConverter.hexToByte(torrentHash), peerId, howMuchPeersWeWant, (short) tcpPort);
 
         Function<ByteBuffer, AnnounceResponse> createResponse = (ByteBuffer response) ->
                 new AnnounceResponse(this,

### 2018-03-02 src/main/java/main/peer/PeersCommunicator.java
PeersCommunicator.java: 1. changed names of isChoked -> peerChokesMe,isInterestedInMe -> peerInterestedInMe, peerMessageFlux -> peerMessageResponseFlux. 2. made peerMessageResponseFlux hot-flux because it must be not a cold one because if it's cold then we can listen for messages on the same port multiple times --->> bug. we will activate this flux only if we have at list one subsriber and will we never dispose this flux unless error. even if there are no subsribers, the source will still produce signals. this is because old data may be multiple pieces which is too much memory on the RAM so we

@@ -17,10 +17,10 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
     private Peer peer;
     private BitSet peerPieces;
     private Socket peerSocket;
-    private boolean isChoked;
-    private boolean isInterestedInMe;
+    private boolean peerChokesMe;
+    private boolean peerInterestedInMe;
     private TorrentInfo torrentInfo;
-    private Flux<PeerMessage> peerMessageFlux;
+    private Flux<PeerMessage> peerMessageResponseFlux;
     private Flux<Double> peerDownloadSpeedFlux;
     private Flux<Double> peerUploadSpeedFlux;
     private FluxSink<PieceMessage> outGoingPiecesFluxSink;
@@ -46,17 +46,28 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
                              DataInputStream dataInputStream) {
         assert peerSocket != null;
         this.peer = peer;
-        this.isChoked = false;
-        this.isInterestedInMe = false;
+        this.peerChokesMe = false;
+        this.peerInterestedInMe = false;
         this.peerSocket = peerSocket;
         this.torrentInfo = torrentInfo;
         this.peerPieces = new BitSet(torrentInfo.getPieces().size());
         this.me = new Peer("localhost", peerSocket.getLocalPort());
         this.IWantToCloseConnection = false;
 
-        Flux<PeerMessage> peerMessageResponseFlux = Flux.create((FluxSink<PeerMessage> sink) -> listenForPeerMessages(sink, dataInputStream))
-                .subscribeOn(Schedulers.elastic())
-                .onErrorResume(PeerExceptions.communicationErrors, throwable -> Mono.empty());
+        this.peerMessageResponseFlux =
+                Flux.create((FluxSink<PeerMessage> sink) -> listenForPeerMessages(sink, dataInputStream))
+                        // it is important to publish from source on different thread then the
+                        // subscription to this source's thread every time because:
+                        // if not and we subscribe to this specific source multiple times then only the
+                        // first subscription will be activated and the source will never end
+                        .subscribeOn(Schedulers.elastic())
+                        .onErrorResume(PeerExceptions.communicationErrors, throwable -> Mono.empty())
+                        // there are multiple subscribers to this source (every specific peer-message flux).
[…]

### 2018-03-02 src/test/java/com/steps/MyStepdefs.java
refactored the tests to the latest changes in the source code.

@@ -3,7 +3,6 @@ package com.steps;
 import com.utils.*;
 import cucumber.api.java.en.Given;
 import cucumber.api.java.en.Then;
-import main.AppConfig;
 import main.TorrentInfo;
 import main.peer.InitializePeersCommunication;
 import main.peer.Peer;
@@ -42,8 +41,7 @@ public class MyStepdefs {
                 .thenReturn(torrentInfo.getTorrentInfoHash());
         Mockito.when(this.torrentInfo.getTrackerList())
                 .thenReturn(torrentInfo.getTrackerList());
-        this.initializePeersCommunication = new InitializePeersCommunication(this.torrentInfo,
-                AppConfig.getInstance().getTcpPortListeningForPeersMessages());
+        this.initializePeersCommunication = new InitializePeersCommunication(this.torrentInfo);
         this.trackerProvider = new TrackerProvider(this.torrentInfo);
         this.peersProvider = new PeersProvider(this.torrentInfo, this.trackerProvider, this.initializePeersCommunication);
     }
@@ -70,8 +68,7 @@ public class MyStepdefs {
                     Mockito.when(this.torrentInfo.getTrackerList()).thenReturn(trackers);
                 });
         this.initializePeersCommunication.stopListenForNewPeers();
-        this.initializePeersCommunication = new InitializePeersCommunication(this.torrentInfo,
-                AppConfig.getInstance().getTcpPortListeningForPeersMessages());
+        this.initializePeersCommunication = new InitializePeersCommunication(this.torrentInfo);
     }
 
     @Given("^additional invalid url of a tracker$")
@@ -128,7 +125,8 @@ public class MyStepdefs {
                                         .flatMap(messageWeNeedToSend -> {
                                             switch (messageWeNeedToSend.getTrackerRequestType()) {
                                                 case Announce:
-                                                    return trackerConnection.announce(this.torrentInfo.getTorrentInfoHash());
+                                                    return trackerConnection.announce(this.torrentInfo.getTorrentInfoHash(),
+                                                            this.initializePeersCommunication.getTcpPort());
                                                 case Scrape:
                                                     return trackerConnection.scrape(Collections.singletonList(this.torrentInfo.getTorrentInfoHash()));
                                                 default:
@@ -162,7 +160,6 @@ public class MyStepdefs {
[…]

### 2018-03-03 src/main/java/main/downloader/TorrentDownloader.java
implemented the new feature file and changed the API for SendPeerMessage interface to return the PeersCommunicator object which called the send operation. This is for chaining multiple sends in the same pipeline and to be able to switch to receivePeerMessageFlux without breaking the pipeline.
Also updated the tests as needed.

@@ -4,13 +4,14 @@ import main.TorrentInfo;
 import main.peer.InitializePeersCommunication;
 import main.peer.PeersCommunicator;
 import main.peer.PeersProvider;
-import main.peer.peerMessages.PeerMessage;
+import main.peer.ReceivePeerMessages;
+import main.peer.peerMessages.*;
 import main.tracker.TrackerConnection;
 import main.tracker.TrackerProvider;
 import reactor.core.publisher.ConnectableFlux;
 import reactor.core.publisher.Flux;
 
-public abstract class TorrentDownloader implements DownloadControl {
+public abstract class TorrentDownloader implements DownloadControl, ReceivePeerMessages {
 
     private TorrentInfo torrentInfo;
     private Downloader downloader;
@@ -20,6 +21,23 @@ public abstract class TorrentDownloader implements DownloadControl {
     private Flux<Double> torrentUploadSpeedFlux;
     private Flux<PeersCommunicator> peersCommunicatorFlux;
     private ConnectableFlux<TrackerConnection> trackerConnectionConnectableFlux;
+
+    // receive messages:
+
+    private Flux<PeerMessage> peerMessageResponseFlux;
+
+    private Flux<BitFieldMessage> bitFieldMessageResponseFlux;
+    private Flux<CancelMessage> cancelMessageResponseFlux;
+    private Flux<ChokeMessage> chokeMessageResponseFlux;
+    private Flux<ExtendedMessage> extendedMessageResponseFlux;
+    private Flux<HaveMessage> haveMessageResponseFlux;
+    private Flux<InterestedMessage> interestedMessageResponseFlux;
+    private Flux<KeepAliveMessage> keepMessageResponseFlux;
+    private Flux<NotInterestedMessage> notInterestedMessageResponseFlux;
+    private Flux<PieceMessage> pieceMessageResponseFlux;
+    private Flux<PortMessage> portMessageResponseFlux;
+    private Flux<RequestMessage> requestMessageResponseFlux;
+    private Flux<UnchokeMessage> unchokeMessageResponseFlux;
 
     public TorrentDownloader(TorrentInfo torrentInfo, Downloader downloader,
                              TrackerProvider trackerProvider, PeersProvider peersProvider,
@@ -31,6 +49,45 @@ public abstract class TorrentDownloader implements DownloadControl {
         this.peersProvider = peersProvider;
         this.peersCommunicatorFlux = peersCommunicatorFlux;
[…]

### 2018-03-03 src/main/java/main/downloader/TorrentDownloaderImpl.java

@@ -3,7 +3,6 @@ package main.downloader;
 import main.TorrentInfo;
 import main.peer.PeersCommunicator;
 import main.peer.PeersProvider;
-import main.peer.peerMessages.PeerMessage;
 import main.tracker.TrackerConnection;
 import main.tracker.TrackerProvider;
 import reactor.core.publisher.ConnectableFlux;
@@ -27,14 +26,24 @@ public class TorrentDownloaderImpl extends TorrentDownloader {
         super(torrentInfo, downloader);
     }
 
-    @Override
-    public Flux<PeerMessage> getPeersMessagesFlux() {
-        return super.getPeersCommunicatorFlux()
-                .flatMap(PeersCommunicator::receive);
+    private void algorithm() {
+        this.getPeersCommunicatorFlux()
+                .subscribe(peersCommunicator -> {
+                    peersCommunicator.sendInterestedMessage()
+                            .subscribe(null, null, () -> {
+                                peersCommunicator.getHaveMessageResponseFlux()
+                                        .flatMap(aVoid -> peersCommunicator.getHaveMessageResponseFlux())
+                                        .take(1)
+                                        .flatMap(haveMessage ->
+                                                peersCommunicator.sendRequestMessage(haveMessage.getPieceIndex(), 0, 16000))
+                                        .subscribe();
+                            });
+                });
     }
 
     @Override
     public void start() {
+        algorithm();
         this.getTrackerConnectionConnectableFlux().connect();
     }
 

### 2018-03-03 src/main/java/main/peer/InitializePeersCommunication.java

@@ -5,10 +5,7 @@ import main.HexByteConverter;
 import main.TorrentInfo;
 import main.peer.peerMessages.HandShake;
 import main.tracker.BadResponseException;
-import reactor.core.publisher.Flux;
-import reactor.core.publisher.FluxSink;
-import reactor.core.publisher.Mono;
-import reactor.core.publisher.MonoSink;
+import reactor.core.publisher.*;
 import reactor.core.scheduler.Schedulers;
 
 import java.io.DataInputStream;
@@ -22,17 +19,20 @@ public class InitializePeersCommunication {
 
     private TorrentInfo torrentInfo;
     private ServerSocket listenToPeerConnection;
-    private final Flux<PeersCommunicator> allPeersCommunicatorFlux;
+    private final ConnectableFlux<PeersCommunicator> allPeersCommunicatorFlux;
 
-    public InitializePeersCommunication(TorrentInfo torrentInfo) {
+    private Integer tcpPort;
+
+    public InitializePeersCommunication(TorrentInfo torrentInfo, Integer tcpPort) {
         this.torrentInfo = torrentInfo;
-        try {
-            this.listenToPeerConnection = new ServerSocket(getFreePortOnLocalMachine());
-        } catch (IOException e) {
-            // TODO: do something with this shit
-            e.printStackTrace();
-        }
+        this.tcpPort = tcpPort;
         this.allPeersCommunicatorFlux = Flux.create((FluxSink<PeersCommunicator> sink) -> {
+            try {
+                this.listenToPeerConnection = new ServerSocket(this.tcpPort);
+            } catch (IOException e) {
+                // TODO: do something with this shit
+                e.printStackTrace();
+            }
             while (!this.listenToPeerConnection.isClosed() && !sink.isCancelled())
                 try {
                     Socket peerSocket = this.listenToPeerConnection.accept();
@@ -47,12 +47,8 @@ public class InitializePeersCommunication {
                         e1.printStackTrace();
                     }
                 }
-        })
-                .subscribeOn(Schedulers.elastic());
-    }
-
-    public int getFreePortOnLocalMachine() {
-        return 9097;
+        }).subscribeOn(Schedulers.elastic())
+                .publish();
     }
 
     public Mono<PeersCommunicator> connectToPeer(Peer peer) {
@@ -79,8 +75,6 @@ public class InitializePeersCommunication {
                     return;
                 } else {
                     // all went well, I accept this connection.
-//                    Peer me = new Peer("localhost", peerSocket.getLocalPort());
[…]

### 2018-03-03 src/main/java/main/peer/PeersCommunicator.java

@@ -20,12 +20,13 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
     private boolean peerChokesMe;
     private boolean peerInterestedInMe;
     private TorrentInfo torrentInfo;
-    private Flux<PeerMessage> peerMessageResponseFlux;
     private Flux<Double> peerDownloadSpeedFlux;
     private Flux<Double> peerUploadSpeedFlux;
     private FluxSink<PieceMessage> outGoingPiecesFluxSink;
 
     // receive messages:
+
+    private Flux<PeerMessage> peerMessageResponseFlux;
 
     private Flux<BitFieldMessage> bitFieldMessageResponseFlux;
     private Flux<CancelMessage> cancelMessageResponseFlux;
@@ -68,53 +69,56 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
                         // **any** subscriber to **this** source may start the source to produce signals
                         // to him and everyone else.
                         .autoConnect(1);
+        ;
 
-        this.bitFieldMessageResponseFlux = peerMessageResponseFlux
+        this.bitFieldMessageResponseFlux = this.peerMessageResponseFlux
                 .filter(peerMessage -> peerMessage instanceof BitFieldMessage)
                 .cast(BitFieldMessage.class)
                 .doOnNext(bitFieldMessage -> this.peerPieces.or(bitFieldMessage.getPieces()));
 
-        this.cancelMessageResponseFlux = peerMessageResponseFlux
+        this.cancelMessageResponseFlux = this.peerMessageResponseFlux
                 .filter(peerMessage -> peerMessage instanceof CancelMessage)
                 .cast(CancelMessage.class);
 
-        this.chokeMessageResponseFlux = peerMessageResponseFlux
+        this.chokeMessageResponseFlux = this.peerMessageResponseFlux
                 .filter(peerMessage -> peerMessage instanceof ChokeMessage)
                 .cast(ChokeMessage.class)
                 .doOnNext(chokeMessage -> this.peerChokesMe = true);
 
-        this.extendedMessageResponseFlux = peerMessageResponseFlux
+        this.extendedMessageResponseFlux = this.peerMessageResponseFlux
                 .filter(peerMessage -> peerMessage instanceof ExtendedMessage)
                 .cast(ExtendedMessage.class);
 
-        this.haveMessageResponseFlux = peerMessageResponseFlux
+        this.haveMessageResponseFlux = this.peerMessageResponseFlux
[…]

### 2018-03-03 src/main/java/main/peer/PeersProvider.java

@@ -1,13 +1,11 @@
 package main.peer;
 
-import lombok.SneakyThrows;
 import main.TorrentInfo;
 import main.tracker.TrackerConnection;
 import main.tracker.TrackerProvider;
 import main.tracker.response.AnnounceResponse;
 import org.slf4j.Logger;
 import org.slf4j.LoggerFactory;
-import reactor.core.publisher.ConnectableFlux;
 import reactor.core.publisher.Flux;
 import reactor.core.publisher.Mono;
 import reactor.core.scheduler.Schedulers;
@@ -26,17 +24,6 @@ public class PeersProvider {
         this.initializePeersCommunication = initializePeersCommunication;
     }
 
-    public Flux<Peer> getPeers(TrackerConnection trackerConnection) {
-        return trackerConnection.announce(this.torrentInfo.getTorrentInfoHash(),
-                // unimportant note: this method will not cause the application to listen for new peers on this torrent so
-                // the tcpPort we choose here is useless... we only need this for constructing new
-                // InitializePeersCommunication instance.
-                this.initializePeersCommunication.getTcpPort())
-                .flux()
-                .flatMap(AnnounceResponse::getPeers);
-    }
-
-    @SneakyThrows
     public Mono<PeersCommunicator> connectToPeer(Peer peer) {
         return initializePeersCommunication
                 .connectToPeer(peer)
@@ -58,7 +45,7 @@ public class PeersProvider {
                 .flatMap((Peer peer) -> connectToPeer(peer));
     }
 
-    public Flux<PeersCommunicator> connectToPeers(ConnectableFlux<TrackerConnection> trackerConnectionFlux) {
+    public Flux<PeersCommunicator> connectToPeers(Flux<TrackerConnection> trackerConnectionFlux) {
         return trackerConnectionFlux
                 .flatMap(trackerConnection -> connectToPeers(trackerConnection));
     }

### 2018-03-03 src/main/java/main/peer/ReceivePeerMessages.java

@@ -4,6 +4,8 @@ import main.peer.peerMessages.*;
 import reactor.core.publisher.Flux;
 
 public interface ReceivePeerMessages {
+    Flux<PeerMessage> getPeerMessageResponseFlux();
+
     Flux<BitFieldMessage> getBitFieldMessageResponseFlux();
 
     Flux<CancelMessage> getCancelMessageResponseFlux();

### 2018-03-03 src/main/java/main/tracker/TrackerCommunication.java

@@ -94,7 +94,6 @@ class TrackerCommunication {
         return Mono.create(sink -> {
             try {
                 DatagramSocket clientSocket = new DatagramSocket();
-                sink.onDispose(() -> clientSocket.close());
                 clientSocket.send(request);
                 sink.success(clientSocket);
 
@@ -107,7 +106,6 @@ class TrackerCommunication {
     private static Mono<ByteBuffer> receiveResponse(DatagramSocket trackerSocket) {
         return Mono.create(sink -> {
             try {
-                sink.onDispose(() -> trackerSocket.close());
                 byte[] receiveData = new byte[1000];
                 DatagramPacket receivePacket = new DatagramPacket(receiveData, receiveData.length);
                 trackerSocket.setSoTimeout(1000);

### 2018-03-03 src/test/java/com/steps/MyStepdefs.java

@@ -9,11 +9,14 @@ import main.peer.Peer;
 import main.peer.PeersCommunicator;
 import main.peer.PeersProvider;
 import main.peer.peerMessages.PeerMessage;
+import main.peer.peerMessages.PieceMessage;
 import main.tracker.BadResponseException;
 import main.tracker.Tracker;
+import main.tracker.TrackerConnection;
 import main.tracker.TrackerProvider;
 import main.tracker.response.TrackerResponse;
 import org.mockito.Mockito;
+import reactor.core.publisher.ConnectableFlux;
 import reactor.core.publisher.Flux;
 import reactor.core.publisher.Mono;
 import reactor.test.StepVerifier;
@@ -27,10 +30,7 @@ import static org.mockito.Mockito.mock;
 public class MyStepdefs {
 
     private String torrentFilePath;
-    private PeersProvider peersProvider;
-    private TrackerProvider trackerProvider;
     private TorrentInfo torrentInfo = mock(TorrentInfo.class);
-    private InitializePeersCommunication initializePeersCommunication;
 
     @Given("^new torrent file: \"([^\"]*)\"$")
     public void newTorrentFile(String torrentFileName) throws Throwable {
@@ -41,34 +41,27 @@ public class MyStepdefs {
                 .thenReturn(torrentInfo.getTorrentInfoHash());
         Mockito.when(this.torrentInfo.getTrackerList())
                 .thenReturn(torrentInfo.getTrackerList());
-        this.initializePeersCommunication = new InitializePeersCommunication(this.torrentInfo);
-        this.trackerProvider = new TrackerProvider(this.torrentInfo);
-        this.peersProvider = new PeersProvider(this.torrentInfo, this.trackerProvider, this.initializePeersCommunication);
     }
 
     @Given("^additional not-responding trackers to the tracker-list$")
     public void additionalNotRespondingTrackersToTheTrackerListFromFile() throws Throwable {
-        TorrentInfo torrentInfo = Utils.readTorrentFile(this.torrentFilePath);
-        String torrentHashInfo = torrentInfo.getTorrentInfoHash();
-        torrentInfo.getTrackerList()
+        List<Tracker> fakeTrackers = new ArrayList<>();
+
+        // wrong url (but valid url) and a random port
+        fakeTrackers.add(new Tracker("udp", "wrongUrl.com", 8090));
+
+        this.torrentInfo.getTrackerList()
                 .stream()
                 .findFirst()
[…]

### 2018-03-03 src/test/java/com/utils/Utils.java

@@ -15,7 +15,7 @@ public class Utils {
         return new TorrentInfo(TorrentParser.parseTorrent(torrentFilesPath));
     }
 
-    public static Mono<Void> sendFakeMessage(PeerMessageType peerMessageType, PeersCommunicator peersCommunicator) {
+    public static Mono<PeersCommunicator> sendFakeMessage(PeerMessageType peerMessageType, PeersCommunicator peersCommunicator) {
         switch (peerMessageType) {
             case HaveMessage:
                 return peersCommunicator.sendHaveMessage(0);

### 2018-03-03 src/main/java/main/downloader/TorrentDownloader.java
renamed InitializePeersCommunication.java to ConnectToPeer.java

@@ -1,7 +1,7 @@
 package main.downloader;
 
 import main.TorrentInfo;
-import main.peer.InitializePeersCommunication;
+import main.peer.ConnectToPeer;
 import main.peer.PeersCommunicator;
 import main.peer.PeersProvider;
 import main.peer.ReceivePeerMessages;
@@ -107,7 +107,7 @@ public abstract class TorrentDownloader implements DownloadControl, ReceivePeerM
         this(torrentInfo,
                 downloader,
                 trackerProvider.connectToTrackers(),
-                new PeersProvider(torrentInfo, trackerProvider, new InitializePeersCommunication(torrentInfo, -80)),
+                new PeersProvider(torrentInfo, trackerProvider, new ConnectToPeer(torrentInfo, -80)),
                 trackerProvider);
     }
 

### 2018-03-03 src/main/java/main/peer/ConnectToPeer.java

@@ -15,7 +15,7 @@ import java.net.InetSocketAddress;
 import java.net.ServerSocket;
 import java.net.Socket;
 
-public class InitializePeersCommunication {
+public class ConnectToPeer {
 
     private TorrentInfo torrentInfo;
     private ServerSocket listenToPeerConnection;
@@ -23,7 +23,7 @@ public class InitializePeersCommunication {
 
     private Integer tcpPort;
 
-    public InitializePeersCommunication(TorrentInfo torrentInfo, Integer tcpPort) {
+    public ConnectToPeer(TorrentInfo torrentInfo, Integer tcpPort) {
         this.torrentInfo = torrentInfo;
         this.tcpPort = tcpPort;
         this.allPeersCommunicatorFlux = Flux.create((FluxSink<PeersCommunicator> sink) -> {

### 2018-03-03 src/main/java/main/peer/PeersProvider.java

@@ -15,17 +15,17 @@ public class PeersProvider {
 
     private TorrentInfo torrentInfo;
     private TrackerProvider trackerProvider;
-    private InitializePeersCommunication initializePeersCommunication;
+    private ConnectToPeer connectToPeer;
 
     public PeersProvider(TorrentInfo torrentInfo, TrackerProvider trackerProvider,
-                         InitializePeersCommunication initializePeersCommunication) {
+                         ConnectToPeer connectToPeer) {
         this.torrentInfo = torrentInfo;
         this.trackerProvider = trackerProvider;
-        this.initializePeersCommunication = initializePeersCommunication;
+        this.connectToPeer = connectToPeer;
     }
 
     public Mono<PeersCommunicator> connectToPeer(Peer peer) {
-        return initializePeersCommunication
+        return connectToPeer
                 .connectToPeer(peer)
                 .subscribeOn(Schedulers.elastic())
                 .doOnError(PeerExceptions.communicationErrors, error ->
@@ -38,7 +38,7 @@ public class PeersProvider {
     }
 
     public Flux<PeersCommunicator> connectToPeers(TrackerConnection trackerConnection) {
-        return trackerConnection.announce(torrentInfo.getTorrentInfoHash(), this.initializePeersCommunication.getTcpPort())
+        return trackerConnection.announce(torrentInfo.getTorrentInfoHash(), this.connectToPeer.getTcpPort())
                 .flux()
                 .flatMap(AnnounceResponse::getPeers)
                 .distinct()
@@ -54,8 +54,8 @@ public class PeersProvider {
         return connectToPeers(this.trackerProvider.connectToTrackers());
     }
 
-    public InitializePeersCommunication getInitializePeersCommunication() {
-        return initializePeersCommunication;
+    public ConnectToPeer getConnectToPeer() {
+        return connectToPeer;
     }
 
     public TorrentInfo getTorrentInfo() {

### 2018-03-03 src/test/java/com/steps/MyStepdefs.java

@@ -4,7 +4,7 @@ import com.utils.*;
 import cucumber.api.java.en.Given;
 import cucumber.api.java.en.Then;
 import main.TorrentInfo;
-import main.peer.InitializePeersCommunication;
+import main.peer.ConnectToPeer;
 import main.peer.Peer;
 import main.peer.PeersCommunicator;
 import main.peer.PeersProvider;
@@ -81,10 +81,10 @@ public class MyStepdefs {
         // we won't listen for peers so we use illegal port number.
         int tcpPortToListenForPeers = -80;
 
-        InitializePeersCommunication initializePeersCommunication =
-                new InitializePeersCommunication(this.torrentInfo, tcpPortToListenForPeers);
+        ConnectToPeer connectToPeer =
+                new ConnectToPeer(this.torrentInfo, tcpPortToListenForPeers);
 
-        PeersProvider peersProvider = new PeersProvider(this.torrentInfo, trackerProvider, initializePeersCommunication);
+        PeersProvider peersProvider = new PeersProvider(this.torrentInfo, trackerProvider, connectToPeer);
 
         Mono<PeersCommunicator> peersCommunicatorFlux =
                 trackerProvider.connectToTrackers()
@@ -120,11 +120,11 @@ public class MyStepdefs {
         // we won't listen for peers so we use illegal port number.
         int tcpPortToListenForPeers = -80;
 
-        InitializePeersCommunication initializePeersCommunication =
-                new InitializePeersCommunication(this.torrentInfo, tcpPortToListenForPeers);
+        ConnectToPeer connectToPeer =
+                new ConnectToPeer(this.torrentInfo, tcpPortToListenForPeers);
 
         // we must to do for now and if not we get NullPointerException.
-        initializePeersCommunication.listen().subscribe();
+        connectToPeer.listen().subscribe();
 
         Flux<TrackerResponse> actualTrackerResponseFlux =
                 trackerProvider.connectToTrackers()
@@ -138,7 +138,7 @@ public class MyStepdefs {
                                             switch (messageWeNeedToSend.getTrackerRequestType()) {
                                                 case Announce:
                                                     return trackerConnection.announce(this.torrentInfo.getTorrentInfoHash(),
-                                                            initializePeersCommunication.getTcpPort());
+                                                            connectToPeer.getTcpPort());
                                                 case Scrape:
[…]

### 2018-03-03 src/main/java/main/tracker/TrackerConnection.java
added toString method to TrackerConnection class

@@ -53,5 +53,12 @@ public class TrackerConnection extends Tracker {
 
         return TrackerCommunication.communicate(scrapeRequest, createResponse);
     }
+
+    @Override
+    public String toString() {
+        return "TrackerConnection{" +
+                super.toString() +
+                "} ";
+    }
 }
 

### 2018-03-03 src/main/java/main/tracker/TrackerCommunication.java
changed log level of logs in class: TrackerCommunication to debug level.

@@ -45,7 +45,7 @@ class TrackerCommunication {
                     sink.next(response);
                 })
                 .doOnError(TrackerExceptions.communicationErrors, error ->
-                        logger.warn("error signal: (the application will maybe try to send" +
+                        logger.debug("error signal: (the application will maybe try to send" +
                                 " the request again to the same tracker)." +
                                 "\nerror message: " + error.getMessage() + ".\n" +
                                 "error type: " + error.getClass().getName()))
@@ -53,7 +53,7 @@ class TrackerCommunication {
                 // which is defined in sendRequest method.
                 .retry(1, TrackerExceptions.communicationErrors)
                 .doOnError(TrackerExceptions.communicationErrors, error ->
-                        logger.warn("error signal: (the application retried to send" +
+                        logger.debug("error signal: (the application retried to send" +
                                 " a request to the same tracker again and failed)." +
                                 "\nerror message: " + error.getMessage() + ".\n" +
                                 "error type: " + error.getClass().getName()))

### 2018-03-03 src/main/java/main/peer/PeersCommunicator.java
removed debug-logs from class PeersCommunicator

@@ -110,9 +110,7 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
 
         this.pieceMessageResponseFlux = this.peerMessageResponseFlux
                 .filter(peerMessage -> peerMessage instanceof PieceMessage)
-                .doOnNext(pieceMessage -> System.out.println("1 we got new piece!!!!"))
-                .cast(PieceMessage.class)
-                .doOnNext(pieceMessage -> System.out.println("2 we got new piece!!!!"));
+                .cast(PieceMessage.class);
 
         this.portMessageResponseFlux = this.peerMessageResponseFlux
                 .filter(peerMessage -> peerMessage instanceof PortMessage)

### 2018-03-03 src/main/java/main/downloader/TorrentDownloader.java
removed class ConnectToPeer and moved it's only method to: PeersProvider class.

@@ -1,7 +1,6 @@
 package main.downloader;
 
 import main.TorrentInfo;
-import main.peer.ConnectToPeer;
 import main.peer.PeersCommunicator;
 import main.peer.PeersProvider;
 import main.peer.ReceivePeerMessages;
@@ -107,7 +106,7 @@ public abstract class TorrentDownloader implements DownloadControl, ReceivePeerM
         this(torrentInfo,
                 downloader,
                 trackerProvider.connectToTrackers(),
-                new PeersProvider(torrentInfo, trackerProvider, new ConnectToPeer(torrentInfo, -80)),
+                new PeersProvider(torrentInfo, trackerProvider),
                 trackerProvider);
     }
 

### 2018-03-03 src/main/java/main/peer/PeersListener.java

@@ -5,27 +5,25 @@ import main.HexByteConverter;
 import main.TorrentInfo;
 import main.peer.peerMessages.HandShake;
 import main.tracker.BadResponseException;
-import reactor.core.publisher.*;
+import reactor.core.publisher.ConnectableFlux;
+import reactor.core.publisher.Flux;
+import reactor.core.publisher.FluxSink;
 import reactor.core.scheduler.Schedulers;
 
 import java.io.DataInputStream;
 import java.io.IOException;
 import java.io.OutputStream;
-import java.net.InetSocketAddress;
 import java.net.ServerSocket;
 import java.net.Socket;
+import java.util.Optional;
 
-public class ConnectToPeer {
-
-    private TorrentInfo torrentInfo;
+public class PeersListener {
+    private Integer tcpPort = 80;
     private ServerSocket listenToPeerConnection;
-    private final ConnectableFlux<PeersCommunicator> allPeersCommunicatorFlux;
+    private ConnectableFlux<PeersCommunicator> allPeersCommunicatorFlux;
 
-    private Integer tcpPort;
+    private PeersListener() {
 
-    public ConnectToPeer(TorrentInfo torrentInfo, Integer tcpPort) {
-        this.torrentInfo = torrentInfo;
-        this.tcpPort = tcpPort;
         this.allPeersCommunicatorFlux = Flux.create((FluxSink<PeersCommunicator> sink) -> {
             try {
                 this.listenToPeerConnection = new ServerSocket(this.tcpPort);
@@ -49,45 +47,6 @@ public class ConnectToPeer {
                 }
         }).subscribeOn(Schedulers.elastic())
                 .publish();
-    }
-
-    public Mono<PeersCommunicator> connectToPeer(Peer peer) {
-        return Mono.create((MonoSink<PeersCommunicator> sink) -> {
-            Socket peerSocket = new Socket();
-            try {
-                peerSocket.connect(new InetSocketAddress(peer.getPeerIp(), peer.getPeerPort()), 1000 * 10);
-                DataInputStream receiveMessages = new DataInputStream(peerSocket.getInputStream());
-                OutputStream sendMessages = peerSocket.getOutputStream();
-
-                // firstly, we need to send Handshake message to the peer and receive Handshake back.
-                HandShake handShakeSending = new HandShake(HexByteConverter.hexToByte(this.torrentInfo.getTorrentInfoHash()), AppConfig.getInstance().getPeerId().getBytes());
[…]

### 2018-03-03 src/main/java/main/peer/PeersProvider.java

@@ -1,6 +1,10 @@
 package main.peer;
 
+import main.AppConfig;
+import main.HexByteConverter;
 import main.TorrentInfo;
+import main.peer.peerMessages.HandShake;
+import main.tracker.BadResponseException;
 import main.tracker.TrackerConnection;
 import main.tracker.TrackerProvider;
 import main.tracker.response.AnnounceResponse;
@@ -8,41 +12,82 @@ import org.slf4j.Logger;
 import org.slf4j.LoggerFactory;
 import reactor.core.publisher.Flux;
 import reactor.core.publisher.Mono;
+import reactor.core.publisher.MonoSink;
 import reactor.core.scheduler.Schedulers;
+
+import java.io.DataInputStream;
+import java.io.IOException;
+import java.io.OutputStream;
+import java.net.InetSocketAddress;
+import java.net.Socket;
 
 public class PeersProvider {
     private static Logger logger = LoggerFactory.getLogger(PeersProvider.class);
 
     private TorrentInfo torrentInfo;
     private TrackerProvider trackerProvider;
-    private ConnectToPeer connectToPeer;
 
-    public PeersProvider(TorrentInfo torrentInfo, TrackerProvider trackerProvider,
-                         ConnectToPeer connectToPeer) {
+    public PeersProvider(TorrentInfo torrentInfo, TrackerProvider trackerProvider) {
         this.torrentInfo = torrentInfo;
         this.trackerProvider = trackerProvider;
-        this.connectToPeer = connectToPeer;
     }
 
     public Mono<PeersCommunicator> connectToPeer(Peer peer) {
-        return connectToPeer
-                .connectToPeer(peer)
-                .subscribeOn(Schedulers.elastic())
-                .doOnError(PeerExceptions.communicationErrors, error ->
-                        logger.warn("error signal: (the application failed to connect to a peer." +
-                                " the application will try to connect to the next available peer).\n" +
-                                "peer: " + peer.toString() + "\n" +
-                                "error message: " + error.getMessage() + ".\n" +
-                                "error type: " + error.getClass().getName()))
+        return Mono.create((MonoSink<PeersCommunicator> sink) -> {
+            Socket peerSocket = new Socket();
+            try {
+                peerSocket.connect(new InetSocketAddress(peer.getPeerIp(), peer.getPeerPort()), 1000 * 10);
+                DataInputStream receiveMessages = new DataInputStream(peerSocket.getInputStream());
[…]

### 2018-03-03 src/test/java/com/steps/MyStepdefs.java
changed test due to the deletion of class: ConnectToPeers

@@ -1,12 +1,13 @@
 package com.steps;
 
 import com.utils.*;
+import cucumber.api.java.Before;
 import cucumber.api.java.en.Given;
 import cucumber.api.java.en.Then;
 import main.TorrentInfo;
-import main.peer.ConnectToPeer;
 import main.peer.Peer;
 import main.peer.PeersCommunicator;
+import main.peer.PeersListener;
 import main.peer.PeersProvider;
 import main.peer.peerMessages.PeerMessage;
 import main.peer.peerMessages.PieceMessage;
@@ -18,9 +19,12 @@ import main.tracker.response.TrackerResponse;
 import org.mockito.Mockito;
 import reactor.core.publisher.ConnectableFlux;
 import reactor.core.publisher.Flux;
+import reactor.core.publisher.Hooks;
 import reactor.core.publisher.Mono;
 import reactor.test.StepVerifier;
 
+import java.io.IOException;
+import java.net.Socket;
 import java.net.SocketTimeoutException;
 import java.util.*;
 import java.util.function.Predicate;
@@ -31,6 +35,22 @@ public class MyStepdefs {
 
     private String torrentFilePath;
     private TorrentInfo torrentInfo = mock(TorrentInfo.class);
+
+
+    @Before
+    public void fuck() {
+        Hooks.onNextDropped(object -> {
+            if (object instanceof Socket) {
+                Socket socket = (Socket) object;
+                System.out.println("closing socket of: " + socket.getInetAddress().getHostAddress() + " " + socket.getPort());
+                try {
+                    socket.close();
+                } catch (IOException e) {
+                    e.printStackTrace();
+                }
+            }
+        });
+    }
 
     @Given("^new torrent file: \"([^\"]*)\"$")
     public void newTorrentFile(String torrentFileName) throws Throwable {
@@ -77,14 +97,7 @@ public class MyStepdefs {
     @Then("^application send and receive Handshake from the same random peer$")
     public void applicationSendAndReceiveHandshakeFromTheSameRandomPeer() throws Throwable {
         TrackerProvider trackerProvider = new TrackerProvider(this.torrentInfo);
-
-        // we won't listen for peers so we use illegal port number.
-        int tcpPortToListenForPeers = -80;
-
-        ConnectToPeer connectToPeer =
-                new ConnectToPeer(this.torrentInfo, tcpPortToListenForPeers);
-
[…]

### 2018-03-05 paper/paper.tex
change of variable names and other things

@@
     BitTorrent is a peer-to-peer protocol, which means that the computers in a BitTorrent “swarm” (a group of computers downloading and uploading the same torrent) transfer data between each other without the need for a central server, where all the information passes through a particular server.
-    The tracker server keeps track of where file copies reside on peer machines, which ones are available at the time of the clients request, and helps coordinate efficient transmission and reassembly of the copied file.
+    The trackerUrl server keeps track of where file copies reside on peer machines, which ones are available at the time of the clients request, and helps coordinate efficient transmission and reassembly of the copied file.
 
@@
 
-    A server who is responsible for saving the leechers (threads which  are attempting to download a torrent) and seeders (leechers who finished downloading the torrent) information is called a tracker.
+    A server who is responsible for saving the leechers (threads which  are attempting to download a torrent) and seeders (leechers who finished downloading the torrent) information is called a trackerUrl.
 When a new leecher wants to download, it sends a request to one of the available trackers in the torrent file and asks for all the peers (leechers and seeders).
@@
 
-    It is important to note that the tracker is referring to every peer by peer-public-ip.
+    It is important to note that the trackerUrl is referring to every peer by peer-public-ip.
 
@@
 
-    Once a leecher is getting a response from the tracker about a request to a specific torrent's peer list, the leecher's BitTorrent client software downloads the pieces of the files.
+    Once a leecher is getting a response from the trackerUrl about a request to a specific torrent's peer list, the leecher's BitTorrent client software downloads the pieces of the files.
 Each file in the torrent is divided into small information chunks called pieces.
@@
 
-    Because multiple machines listen to the same port in the same network, we need to be able to get a response from the WAN to the LAN.
-In short, \textbf{NAT} is a method of remapping a public IP address and a port number to a private ip address and a port number and vice versa.
+    Because multiple machines listen to the same udpPort in the same network, we need to be able to get a response from the WAN to the LAN.
+In short, \textbf{NAT} is a method of remapping a public IP address and a udpPort number to a private ip address and a udpPort number and vice versa.
 The majority of NATs map multiple private hosts to one publicly exposed IP address.
@@
 As traffic passes from the local network to the Internet, the source address in each packet is translated on the fly from a private address to the public address.
-The router tracks basic data about each active connection (particularly the destination address and port).
+The router tracks basic data about each active connection (particularly the destination address and udpPort).
 When a reply returns to the router, it uses the connection tracking data it stored during The outbound phase to determine the private address on the internal network to which to forward the reply.
@@
 
-    A Bittorrent client application listens to a specific port in every machine.
-To be able to add this port to the NAT in its router, one must use \textbf{universal plug in play (UPnP)} to avoid manually adding a port and a IP address to the NAT.
+    A Bittorrent client application listens to a specific udpPort in every machine.
+To be able to add this udpPort to the NAT in its router, one must use \textbf{universal plug in play (UPnP)} to avoid manually adding a udpPort and a IP address to the NAT.
 The UPNP is a way to configure the NAT in any programming language.
-Telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.
+Telling the router which computer to forward a connection to is called \textbf{udpPort forwarding}, each server based application has a udpPort number it works through, its udpPort number is very useful in giving the router the information it needs to forward a connection.
 
@@
   \begin{flushleft}
-    1. \href{http://www.rasterbar.com/products/libtorrent/udp_tracker_protocol.html}{udp tracker protocol}
+    1. \href{http://www.rasterbar.com/products/libtorrent/udp_tracker_protocol.html}{udp trackerUrl protocol}
 

### 2018-03-05 src/main/java/main/App.java

@@ -52,12 +52,12 @@ class App {
 
 
 //    torrent hash: af1f3dbc5d5baeaf83f812e06aa91bbd7b55cce8
-//    udp://tracker.coppersurfer.tk:6969/scrape
-//    udp://9.rarbg.com:2710/scrape
+//    udp://tracker.coppersurfer.tk:6969/scrapeMono
+//    udp://9.rarbg.com:2710/scrapeMono
 //    udp://p4p.arenabg.com:1337
 //    udp://tracker.leechers-paradise.org:6969
 //    udp://tracker.internetwarriors.net:1337
-//    udp://tracker.opentrackr.org:1337/scrape
+//    udp://tracker.opentrackr.org:1337/scrapeMono
 
 //    Peer(ipAddress=35.160.55.32, tcpPort=8104)
 //    Peer(ipAddress=52.59.116.245, tcpPort=8114)

### 2018-03-05 src/main/java/main/TorrentInfo.java

@@ -55,12 +55,12 @@ public class TorrentInfo {
 
 
     public List<Tracker> getTrackerList() {
-        // tracker pattern example: udp://tracker.coppersurfer.tk:6969/scrape
+        // tracker pattern example: udp://tracker.coppersurfer.tk:6969/scrapeMono
         String trackerPattern = "^(.*)://(\\d*\\.)?(.*):(\\d*)(.*)?$";
 
         return this.torrent.getAnnounceList()
                 .stream()
-                .filter((String tracker) -> !tracker.equals("udp://9.rarbg.com:2710/scrape")) // problematic tracker !!!!
+                .filter((String tracker) -> !tracker.equals("udp://9.rarbg.com:2710/scrapeMono")) // problematic tracker !!!!
                 .map((String tracker) -> Pattern.compile(trackerPattern).matcher(tracker))
                 .filter(Matcher::matches)
                 .map((Matcher matcher) -> new Tracker(matcher.group(1), matcher.group(3), Integer.parseInt(matcher.group(4))))

### 2018-03-05 src/main/java/main/downloader/TorrentDownloader.java

@@ -105,7 +105,7 @@ public abstract class TorrentDownloader implements DownloadControl, ReceivePeerM
     public TorrentDownloader(TorrentInfo torrentInfo, Downloader downloader, TrackerProvider trackerProvider) {
         this(torrentInfo,
                 downloader,
-                trackerProvider.connectToTrackers(),
+                trackerProvider.connectToTrackersFlux(),
                 new PeersProvider(torrentInfo, trackerProvider),
                 trackerProvider);
     }

### 2018-03-05 src/main/java/main/peer/PeersCommunicator.java

@@ -62,6 +62,7 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
                         // if not and we subscribe to this specific source multiple times then only the
                         // first subscription will be activated and the source will never end
                         .subscribeOn(Schedulers.elastic())
+
                         .onErrorResume(PeerExceptions.communicationErrors, throwable -> Mono.empty())
                         // there are multiple subscribers to this source (every specific peer-message flux).
                         // all of them must get the same message and not activate this source more then once.

### 2018-03-05 src/main/java/main/peer/PeersListener.java

@@ -20,11 +20,11 @@ import java.util.Optional;
 public class PeersListener {
     private Integer tcpPort = 80;
     private ServerSocket listenToPeerConnection;
-    private ConnectableFlux<PeersCommunicator> allPeersCommunicatorFlux;
+    private ConnectableFlux<PeersCommunicator> peersConnectedToMeFlux;
 
     private PeersListener() {
 
-        this.allPeersCommunicatorFlux = Flux.create((FluxSink<PeersCommunicator> sink) -> {
+        this.peersConnectedToMeFlux = Flux.create((FluxSink<PeersCommunicator> sink) -> {
             try {
                 this.listenToPeerConnection = new ServerSocket(this.tcpPort);
             } catch (IOException e) {
@@ -32,13 +32,13 @@ public class PeersListener {
                 e.printStackTrace();
             }
             while (!this.listenToPeerConnection.isClosed() && !sink.isCancelled())
-                try {
-                    Socket peerSocket = this.listenToPeerConnection.accept();
-                    // the following method will do sink.next if the connect operation succeed.
-                    acceptPeerConnection(peerSocket, sink);
-                } catch (IOException e) {
-                    sink.error(e);
-                    try {
+                        try {
+                            Socket peerSocket = this.listenToPeerConnection.accept();
+                            // the following method will do sink.next if the connect operation succeed.
+                            acceptPeerConnection(peerSocket, sink);
+                        } catch (IOException e) {
+                            sink.error(e);
+                            try {
                         this.listenToPeerConnection.close();
                     } catch (IOException e1) {
                         // TODO: do something with this shit
@@ -120,5 +120,9 @@ public class PeersListener {
 
     public static PeersListener getInstance() {
         return instance;
+    }
+
+    public ConnectableFlux<PeersCommunicator> getPeersConnectedToMeFlux() {
+        return peersConnectedToMeFlux;
     }
 }

### 2018-03-05 src/main/java/main/peer/PeersProvider.java

@@ -32,7 +32,7 @@ public class PeersProvider {
         this.trackerProvider = trackerProvider;
     }
 
-    public Mono<PeersCommunicator> connectToPeer(Peer peer) {
+    public Mono<PeersCommunicator> connectToPeerMono(Peer peer) {
         return Mono.create((MonoSink<PeersCommunicator> sink) -> {
             Socket peerSocket = new Socket();
             try {
@@ -80,23 +80,22 @@ public class PeersProvider {
                 .onErrorResume(PeerExceptions.communicationErrors, error -> Mono.empty());
     }
 
-    public Flux<PeersCommunicator> connectToPeers(TrackerConnection trackerConnection) {
-        return trackerConnection.announce(torrentInfo.getTorrentInfoHash(), PeersListener.getInstance().getTcpPort())
+    public Flux<Peer> connectToPeers(TrackerConnection trackerConnection) {
+        return trackerConnection.announceMono(torrentInfo.getTorrentInfoHash(), PeersListener.getInstance().getTcpPort())
                 .flux()
-                .flatMap(AnnounceResponse::getPeers)
-                .distinct()
-                .flatMap((Peer peer) -> connectToPeer(peer))
-
-                .doOnNext(peersCommunicator -> System.out.println("connected to peer: " + peersCommunicator.toString()));
+                .flatMap(AnnounceResponse::getPeersFlux);
     }
 
     public Flux<PeersCommunicator> connectToPeers(Flux<TrackerConnection> trackerConnectionFlux) {
         return trackerConnectionFlux
-                .flatMap(trackerConnection -> connectToPeers(trackerConnection));
+                .flatMap(trackerConnection -> connectToPeers(trackerConnection))
+                .distinct()
+                .flatMap((Peer peer) -> connectToPeerMono(peer))
+                .doOnNext(peersCommunicator -> System.out.println("connected to peer: " + peersCommunicator.toString()));
     }
 
     public Flux<PeersCommunicator> connectToPeers() {
-        return connectToPeers(this.trackerProvider.connectToTrackers());
+        return connectToPeers(this.trackerProvider.connectToTrackersFlux());
     }
 
     public TorrentInfo getTorrentInfo() {

### 2018-03-05 src/main/java/main/tracker/TrackerCommunication.java

@@ -20,12 +20,12 @@ class TrackerCommunication {
     private static Logger logger = LoggerFactory.getLogger(TrackerCommunication.class);
 
     public static <Request extends TrackerRequest, Response extends TrackerResponse>
-    Mono<Response> communicate(Request request, Function<ByteBuffer, Response> createResponse) {
-        return sendRequest(request)
+    Mono<Response> communicateMono(Request request, Function<ByteBuffer, Response> createResponse) {
+        return sendRequestMono(request)
                 // before we map to response bytes to response object, check if the response is ErrorResponse
                 // by actionNumber. If yes, create error-signal, else forward the signal.
                 .flatMap((DatagramSocket trackerSocket) ->
-                        receiveResponse(trackerSocket)
+                        receiveResponseMono(trackerSocket)
                                 .handle((ByteBuffer response, SynchronousSink<ByteBuffer> sink) -> {
                                     if (ErrorResponse.isErrorResponse(response.array())) {
                                         ErrorResponse errorResponse = new ErrorResponse(request.getTracker(), response.array());
@@ -38,11 +38,11 @@ class TrackerCommunication {
                     if (request.getTransactionId() != response.getTransactionId() ||
                             request.getActionNumber() != response.getActionNumber())
                         sink.error(new BadResponseException("response's transaction-id is" +
-                                " not equal to the request's transaction-id."));
-                    if (request.getActionNumber() != response.getActionNumber())
+                            " not equal to the request's transaction-id."));
+                    else if (request.getActionNumber() != response.getActionNumber())
                         sink.error(new BadResponseException("response's action-number is" +
                                 " not equal to the request's action-number."));
-                    sink.next(response);
+                    else sink.next(response);
                 })
                 .doOnError(TrackerExceptions.communicationErrors, error ->
                         logger.debug("error signal: (the application will maybe try to send" +
@@ -50,7 +50,7 @@ class TrackerCommunication {
                                 "\nerror message: " + error.getMessage() + ".\n" +
                                 "error type: " + error.getClass().getName()))
                 // the retry operation will run the first, ever created, publisher again
-                // which is defined in sendRequest method.
+                // which is defined in sendRequestMono method.
                 .retry(1, TrackerExceptions.communicationErrors)
[…]

### 2018-03-05 src/main/java/main/tracker/TrackerProvider.java

@@ -18,21 +18,21 @@ public class TrackerProvider {
         this.torrentInfo = torrentInfo;
     }
 
-    public Mono<TrackerConnection> connectToTracker(Tracker tracker) {
+    public Mono<TrackerConnection> connectToTrackerMono(Tracker tracker) {
         ConnectRequest connectRequest = new ConnectRequest(tracker, 123456);
 
         Function<ByteBuffer, ConnectResponse> createConnectResponse = (ByteBuffer response) ->
                 new ConnectResponse(tracker, response.array());
 
-        return TrackerCommunication.communicate(connectRequest, createConnectResponse)
+        return TrackerCommunication.communicateMono(connectRequest, createConnectResponse)
                 .subscribeOn(Schedulers.elastic())
                 .onErrorResume(TrackerExceptions.communicationErrors, error -> Mono.empty())
                 .map(connectResponse -> new TrackerConnection(connectResponse));
     }
 
-    public ConnectableFlux<TrackerConnection> connectToTrackers() {
+    public ConnectableFlux<TrackerConnection> connectToTrackersFlux() {
         return Flux.fromIterable(this.torrentInfo.getTrackerList())
-                .flatMap(tracker -> connectToTracker(tracker))
+                .flatMap(tracker -> connectToTrackerMono(tracker))
                 .publish();
     }
 

### 2018-03-05 src/main/java/main/tracker/response/AnnounceResponse.java

@@ -21,13 +21,13 @@ public class AnnounceResponse extends TrackerResponse {
     private final int seedersAmount;
     private final List<Peer> peers;
 
-    public Flux<Peer> getPeers() {
+    public Flux<Peer> getPeersFlux() {
         return Flux.fromStream(peers.stream());
     }
 
     /**
      * Offset      Size            Name            Value
-     * 0           32-bit integer  action          1 // scrape
+     * 0           32-bit integer  action          1 // scrapeMono
      * 4           32-bit integer  transaction_id
      * 8           32-bit integer  interval
      * 12          32-bit integer  leechersAmount

### 2018-03-05 src/main/java/main/tracker/response/ScrapeResponse.java

@@ -28,7 +28,7 @@ public class ScrapeResponse extends TrackerResponse {
 
     /**
      * Offset      Size            Name            Value
-     * 0           32-bit integer  action          2 // scrape
+     * 0           32-bit integer  action          2 // scrapeMono
      * 4           32-bit integer  transaction_id
      * 8 + 12 * n  32-bit integer  downloaded
      * ?           32-bit integer  complete
@@ -36,7 +36,7 @@ public class ScrapeResponse extends TrackerResponse {
      * 8 + 12 * N
      *
      * @param response          what the tracker sent me back.
-     * @param torrentInfoHashes what torrents I asked about in the scrape request.
+     * @param torrentInfoHashes what torrents I asked about in the scrapeMono request.
      *                          The order is important and I assume that the answer
      *                          will be with the same order as this list.
      */

### 2018-03-05 src/test/java/com/steps/MyStepdefs.java

@@ -11,10 +11,7 @@ import main.peer.PeersListener;
 import main.peer.PeersProvider;
 import main.peer.peerMessages.PeerMessage;
 import main.peer.peerMessages.PieceMessage;
-import main.tracker.BadResponseException;
-import main.tracker.Tracker;
-import main.tracker.TrackerConnection;
-import main.tracker.TrackerProvider;
+import main.tracker.*;
 import main.tracker.response.TrackerResponse;
 import org.mockito.Mockito;
 import reactor.core.publisher.ConnectableFlux;
@@ -73,7 +70,7 @@ public class MyStepdefs {
         this.torrentInfo.getTrackerList()
                 .stream()
                 .findFirst()
-                .ifPresent(tracker -> fakeTrackers.add(new Tracker("udp", tracker.getTracker(), tracker.getPort() + 1))); // wrong port
+                .ifPresent(tracker -> fakeTrackers.add(new Tracker("udp", tracker.getTrackerUrl(), tracker.getUdpPort() + 1))); // wrong port
 
         List<Tracker> trackers = new LinkedList<>();
         trackers.addAll(fakeTrackers);
@@ -99,17 +96,17 @@ public class MyStepdefs {
         TrackerProvider trackerProvider = new TrackerProvider(this.torrentInfo);
         PeersProvider peersProvider = new PeersProvider(this.torrentInfo, trackerProvider);
 
-        Mono<PeersCommunicator> peersCommunicatorFlux =
-                trackerProvider.connectToTrackers()
-                        .refCount(1)
-                        .flatMap(trackerConnection -> peersProvider.connectToPeers(trackerConnection))
-                        .take(1)
-                        .single();
+//        Mono<PeersCommunicator> peersCommunicatorFlux =
+//                trackerProvider.connectToTrackersFlux()
+//                        .refCount(1)
+//                        .flatMap(trackerConnection -> peersProvider.connectToPeers(trackerConnection))
+//                        .take(1)
+//                        .single();
 
-        StepVerifier.create(peersCommunicatorFlux)
-                .expectNextCount(1)
-                .expectComplete()
-                .verify();
+//        StepVerifier.create(peersCommunicatorFlux)
+//                .expectNextCount(1)
+//                .expectComplete()
+//                .verify();
     }
 
     @Then("^application send and receive the following messages from a random tracker:$")
@@ -122,33 +119,27 @@ public class MyStepdefs {
                     " (we are not using it in the tests but " +
[…]

### 2018-03-05 src/main/java/main/downloader/TorrentDownloader.java
changed some methods names to: methodXXXFlux() and methodXXXMono()

@@ -99,7 +99,7 @@ public abstract class TorrentDownloader implements DownloadControl, ReceivePeerM
                              ConnectableFlux<TrackerConnection> trackerConnectionConnectableFlux,
                              PeersProvider peersProvider, TrackerProvider trackerProvider) {
         this(torrentInfo, downloader, trackerProvider, peersProvider, trackerConnectionConnectableFlux,
-                peersProvider.connectToPeers(trackerConnectionConnectableFlux));
+                peersProvider.getPeersFromTrackerFlux(trackerConnectionConnectableFlux));
     }
 
     public TorrentDownloader(TorrentInfo torrentInfo, Downloader downloader, TrackerProvider trackerProvider) {

### 2018-03-05 src/main/java/main/downloader/TorrentDownloaderImpl.java

@@ -33,7 +33,7 @@ public class TorrentDownloaderImpl extends TorrentDownloader {
                             .subscribe(null, null, () -> {
                                 peersCommunicator.getHaveMessageResponseFlux()
                                         .flatMap(aVoid -> peersCommunicator.getHaveMessageResponseFlux())
-                                        .take(1)
+                                        .limitRequest(1)
                                         .flatMap(haveMessage ->
                                                 peersCommunicator.sendRequestMessage(haveMessage.getPieceIndex(), 0, 16000))
                                         .subscribe();

### 2018-03-05 src/main/java/main/peer/PeersProvider.java

@@ -70,7 +70,7 @@ public class PeersProvider {
             }
         }).subscribeOn(Schedulers.elastic())
                 .doOnError(PeerExceptions.communicationErrors, error -> {
-                    System.out.println("failed to connect to peer: " + peer.toString() + ", reason: " + error.getClass().getName());
+                    System.out.println("failed to connect to peer: " + peer.toString() + ", reason: " + error.getClass().getName() + ", error message: " + error.getMessage());
                     logger.debug("error signal: (the application failed to connect to a peer." +
                             " the application will try to connect to the next available peer).\n" +
                             "peer: " + peer.toString() + "\n" +
@@ -80,22 +80,22 @@ public class PeersProvider {
                 .onErrorResume(PeerExceptions.communicationErrors, error -> Mono.empty());
     }
 
-    public Flux<Peer> connectToPeers(TrackerConnection trackerConnection) {
+    public Flux<Peer> getPeersFromTrackerFlux(TrackerConnection trackerConnection) {
         return trackerConnection.announceMono(torrentInfo.getTorrentInfoHash(), PeersListener.getInstance().getTcpPort())
                 .flux()
                 .flatMap(AnnounceResponse::getPeersFlux);
     }
 
-    public Flux<PeersCommunicator> connectToPeers(Flux<TrackerConnection> trackerConnectionFlux) {
+    public Flux<PeersCommunicator> getPeersFromTrackerFlux(Flux<TrackerConnection> trackerConnectionFlux) {
         return trackerConnectionFlux
-                .flatMap(trackerConnection -> connectToPeers(trackerConnection))
+                .flatMap(trackerConnection -> getPeersFromTrackerFlux(trackerConnection))
                 .distinct()
                 .flatMap((Peer peer) -> connectToPeerMono(peer))
                 .doOnNext(peersCommunicator -> System.out.println("connected to peer: " + peersCommunicator.toString()));
     }
 
-    public Flux<PeersCommunicator> connectToPeers() {
-        return connectToPeers(this.trackerProvider.connectToTrackersFlux());
+    public Flux<PeersCommunicator> getPeersFromTrackerFlux() {
+        return getPeersFromTrackerFlux(this.trackerProvider.connectToTrackersFlux());
     }
 
     public TorrentInfo getTorrentInfo() {

### 2018-03-05 src/test/java/com/steps/MyStepdefs.java

@@ -11,10 +11,12 @@ import main.peer.PeersListener;
 import main.peer.PeersProvider;
 import main.peer.peerMessages.PeerMessage;
 import main.peer.peerMessages.PieceMessage;
-import main.tracker.*;
+import main.tracker.Tracker;
+import main.tracker.TrackerConnection;
+import main.tracker.TrackerExceptions;
+import main.tracker.TrackerProvider;
 import main.tracker.response.TrackerResponse;
 import org.mockito.Mockito;
-import reactor.core.publisher.ConnectableFlux;
 import reactor.core.publisher.Flux;
 import reactor.core.publisher.Hooks;
 import reactor.core.publisher.Mono;
@@ -22,9 +24,7 @@ import reactor.test.StepVerifier;
 
 import java.io.IOException;
 import java.net.Socket;
-import java.net.SocketTimeoutException;
 import java.util.*;
-import java.util.function.Predicate;
 
 import static org.mockito.Mockito.mock;
 
@@ -96,17 +96,17 @@ public class MyStepdefs {
         TrackerProvider trackerProvider = new TrackerProvider(this.torrentInfo);
         PeersProvider peersProvider = new PeersProvider(this.torrentInfo, trackerProvider);
 
-//        Mono<PeersCommunicator> peersCommunicatorFlux =
-//                trackerProvider.connectToTrackersFlux()
-//                        .refCount(1)
-//                        .flatMap(trackerConnection -> peersProvider.connectToPeers(trackerConnection))
-//                        .take(1)
-//                        .single();
+        Mono<PeersCommunicator> peersCommunicatorFlux =
+                trackerProvider.connectToTrackersFlux()
+                        .refCount(1)
+                        .transform(trackerConnectionFlux -> peersProvider.getPeersFromTrackerFlux(trackerConnectionFlux))
+                        .limitRequest(1)
+                        .single();
 
-//        StepVerifier.create(peersCommunicatorFlux)
-//                .expectNextCount(1)
-//                .expectComplete()
-//                .verify();
+        StepVerifier.create(peersCommunicatorFlux)
+                .expectNextCount(1)
+                .expectComplete()
+                .verify();
     }
 
     @Then("^application send and receive the following messages from a random tracker:$")
@@ -142,7 +142,7 @@ public class MyStepdefs {
                                         }).onErrorResume(TrackerExceptions.communicationErrors, error -> Mono.empty()))
                         // unimportant note: take is an operation which send "cancel"
[…]

### 2018-03-05 src/main/java/main/App.java
closed every connection which came from a flux/mono which canceled. (peer-connection and tracker-connection)

@@ -2,27 +2,28 @@ package main;
 
 import christophedetroyer.torrent.TorrentParser;
 import lombok.SneakyThrows;
-import main.downloader.Downloader;
-import main.downloader.TorrentDownloader;
-import main.downloader.TorrentDownloaderImpl;
-import main.file.ActiveTorrent;
+import main.tracker.TrackerProvider;
 
 class App {
 
-    // TODO: get all signals which created after a stream disposed or canceled and free their resources!!!
 
     private static void f4() {
 
         TorrentInfo torrentInfo = getTorrentInfo();
-
-        ActiveTorrent activeTorrent = new ActiveTorrent(torrentInfo, null);
-        Downloader downloader = new Downloader(activeTorrent);
-        TorrentDownloader torrentDownloader = new TorrentDownloaderImpl(torrentInfo, downloader);
-
-        torrentDownloader.getPieceMessageResponseFlux()
-                .subscribe(System.out::println, System.out::println, System.out::println);
-
-        torrentDownloader.start();
+        new TrackerProvider(torrentInfo)
+                .connectToTrackersFlux()
+                .autoConnect()
+                .limitRequest(1)
+                .subscribe(System.out::println, Throwable::printStackTrace, () -> System.out.println("finish!!!!"));
+//
+//        ActiveTorrent activeTorrent = new ActiveTorrent(torrentInfo, null);
+//        Downloader downloader = new Downloader(activeTorrent);
+//        TorrentDownloader torrentDownloader = new TorrentDownloaderImpl(torrentInfo, downloader);
+//
+//        torrentDownloader.getPieceMessageResponseFlux()
+//                .subscribe(System.out::println, System.out::println, System.out::println);
+//
+//        torrentDownloader.start();
     }
 
     public static void main(String[] args) throws Exception {

### 2018-03-05 src/main/java/main/peer/PeerMessageFactory.java

@@ -8,7 +8,6 @@ import java.nio.ByteBuffer;
 
 public class PeerMessageFactory {
     public static PeerMessage create(Peer from, Peer to, DataInputStream dataInputStream) throws IOException {
-
         final int messageLengthSize = 4;
         byte[] data1 = new byte[messageLengthSize];
         dataInputStream.readFully(data1);

### 2018-03-05 src/main/java/main/peer/PeersCommunicator.java

@@ -5,9 +5,11 @@ import main.peer.peerMessages.*;
 import reactor.core.publisher.Flux;
 import reactor.core.publisher.FluxSink;
 import reactor.core.publisher.Mono;
+import reactor.core.publisher.MonoSink;
 import reactor.core.scheduler.Schedulers;
 
 import java.io.DataInputStream;
+import java.io.DataOutputStream;
 import java.io.IOException;
 import java.net.Socket;
 import java.util.BitSet;
@@ -23,6 +25,7 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
     private Flux<Double> peerDownloadSpeedFlux;
     private Flux<Double> peerUploadSpeedFlux;
     private FluxSink<PieceMessage> outGoingPiecesFluxSink;
+    private DataOutputStream peerDataOutputStream;
 
     // receive messages:
 
@@ -41,10 +44,8 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
     private Flux<RequestMessage> requestMessageResponseFlux;
     private Flux<UnchokeMessage> unchokeMessageResponseFlux;
 
-    private boolean IWantToCloseConnection;
-
     public PeersCommunicator(TorrentInfo torrentInfo, Peer peer, Socket peerSocket,
-                             DataInputStream dataInputStream) {
+                             DataInputStream dataInputStream, DataOutputStream peerDataOutputStream) {
         assert peerSocket != null;
         this.peer = peer;
         this.peerChokesMe = false;
@@ -53,7 +54,7 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
         this.torrentInfo = torrentInfo;
         this.peerPieces = new BitSet(torrentInfo.getPieces().size());
         this.me = new Peer("localhost", peerSocket.getLocalPort());
-        this.IWantToCloseConnection = false;
+        this.peerDataOutputStream = peerDataOutputStream;
 
         this.peerMessageResponseFlux =
                 Flux.create((FluxSink<PeerMessage> sink) -> listenForPeerMessages(sink, dataInputStream))
@@ -62,7 +63,6 @@ public class PeersCommunicator implements SendPeerMessage, ReceivePeerMessages {
                         // if not and we subscribe to this specific source multiple times then only the
                         // first subscription will be activated and the source will never end
                         .subscribeOn(Schedulers.elastic())
-
[…]

### 2018-03-05 src/main/java/main/peer/PeersListener.java

@@ -11,8 +11,8 @@ import reactor.core.publisher.FluxSink;
 import reactor.core.scheduler.Schedulers;
 
 import java.io.DataInputStream;
+import java.io.DataOutputStream;
 import java.io.IOException;
-import java.io.OutputStream;
 import java.net.ServerSocket;
 import java.net.Socket;
 import java.util.Optional;
@@ -32,34 +32,34 @@ public class PeersListener {
                 e.printStackTrace();
             }
             while (!this.listenToPeerConnection.isClosed() && !sink.isCancelled())
-                        try {
-                            Socket peerSocket = this.listenToPeerConnection.accept();
-                            // the following method will do sink.next if the connect operation succeed.
-                            acceptPeerConnection(peerSocket, sink);
-                        } catch (IOException e) {
-                            sink.error(e);
-                            try {
+                try {
+                    Socket peerSocket = this.listenToPeerConnection.accept();
+                    // the following method will do sink.next if the connect operation succeed.
+                    acceptPeerConnection(peerSocket, sink);
+                } catch (IOException e) {
+                    try {
                         this.listenToPeerConnection.close();
                     } catch (IOException e1) {
                         // TODO: do something with this shit
                         e1.printStackTrace();
                     }
+                    sink.error(e);
                 }
         }).subscribeOn(Schedulers.elastic())
                 .publish();
     }
 
     private void acceptPeerConnection(Socket peerSocket, FluxSink<PeersCommunicator> sink) {
-        OutputStream dataOutputStream = null;
+        DataOutputStream peerDataOutputStream = null;
         try {
-            dataOutputStream = peerSocket.getOutputStream();
+            peerDataOutputStream = new DataOutputStream(peerSocket.getOutputStream());
         } catch (IOException e) {
             sink.error(e);
             return;
         }
-        DataInputStream dataInputStream = null;
+        DataInputStream peerDataInputStream = null;
         try {
-            dataInputStream = new DataInputStream(peerSocket.getInputStream());
+            peerDataInputStream = new DataInputStream(peerSocket.getInputStream());
         } catch (IOException e) {
             sink.error(e);
             return;
@@ -68,7 +68,7 @@ public class PeersListener {
         // firstly, we need to receive Handshake message from the peer and send him Handshake back.
         HandShake handShakeReceived = null;
         try {
-            handShakeReceived = new HandShake(dataInputStream);
[…]

### 2018-03-05 src/main/java/main/peer/PeersProvider.java

@@ -16,8 +16,8 @@ import reactor.core.publisher.MonoSink;
 import reactor.core.scheduler.Schedulers;
 
 import java.io.DataInputStream;
+import java.io.DataOutputStream;
 import java.io.IOException;
-import java.io.OutputStream;
 import java.net.InetSocketAddress;
 import java.net.Socket;
 
@@ -35,10 +35,17 @@ public class PeersProvider {
     public Mono<PeersCommunicator> connectToPeerMono(Peer peer) {
         return Mono.create((MonoSink<PeersCommunicator> sink) -> {
             Socket peerSocket = new Socket();
+            sink.onCancel(() -> {
+                try {
+                    peerSocket.close();
+                } catch (IOException e) {
+                    e.printStackTrace();
+                }
+            });
             try {
                 peerSocket.connect(new InetSocketAddress(peer.getPeerIp(), peer.getPeerPort()), 1000 * 10);
                 DataInputStream receiveMessages = new DataInputStream(peerSocket.getInputStream());
-                OutputStream sendMessages = peerSocket.getOutputStream();
+                DataOutputStream sendMessages = new DataOutputStream(peerSocket.getOutputStream());
 
                 // firstly, we need to send Handshake message to the peer and receive Handshake back.
                 HandShake handShakeSending = new HandShake(HexByteConverter.hexToByte(this.torrentInfo.getTorrentInfoHash()), AppConfig.getInstance().getPeerId().getBytes());
@@ -56,17 +63,19 @@ public class PeersProvider {
                     return;
                 } else {
                     // all went well, I accept this connection.
-                    sink.success(new PeersCommunicator(this.torrentInfo, peer, peerSocket, receiveMessages));
+                    PeersCommunicator peersCommunicator = new PeersCommunicator(this.torrentInfo, peer,
+                            peerSocket, receiveMessages, sendMessages);
+                    sink.success(peersCommunicator);
                     return;
                 }
             } catch (IOException e) {
-                sink.error(e);
                 try {
                     peerSocket.close();
                 } catch (IOException e1) {
                     // TODO: do something with this shit
                     e1.printStackTrace();
                 }
+                sink.error(e);
             }
         }).subscribeOn(Schedulers.elastic())
                 .doOnError(PeerExceptions.communicationErrors, error -> {

### 2018-03-05 src/main/java/main/tracker/TrackerCommunication.java

@@ -38,7 +38,7 @@ class TrackerCommunication {
                     if (request.getTransactionId() != response.getTransactionId() ||
                             request.getActionNumber() != response.getActionNumber())
                         sink.error(new BadResponseException("response's transaction-id is" +
-                            " not equal to the request's transaction-id."));
+                                " not equal to the request's transaction-id."));
                     else if (request.getActionNumber() != response.getActionNumber())
                         sink.error(new BadResponseException("response's action-number is" +
                                 " not equal to the request's action-number."));
@@ -92,12 +92,14 @@ class TrackerCommunication {
 
     private static Mono<DatagramSocket> sendRequestMono(DatagramPacket request) {
         return Mono.create(sink -> {
+            DatagramSocket clientSocket = null;
             try {
-                DatagramSocket clientSocket = new DatagramSocket();
+                clientSocket = new DatagramSocket();
                 clientSocket.send(request);
                 sink.success(clientSocket);
 
             } catch (IOException exception) {
+                clientSocket.close();
                 sink.error(exception);
             }
         });

### 2018-03-05 src/main/java/main/tracker/TrackerProvider.java

@@ -6,7 +6,6 @@ import main.tracker.response.ConnectResponse;
 import reactor.core.publisher.ConnectableFlux;
 import reactor.core.publisher.Flux;
 import reactor.core.publisher.Mono;
-import reactor.core.scheduler.Schedulers;
 
 import java.nio.ByteBuffer;
 import java.util.function.Function;
@@ -25,13 +24,14 @@ public class TrackerProvider {
                 new ConnectResponse(tracker, response.array());
 
         return TrackerCommunication.communicateMono(connectRequest, createConnectResponse)
-                .subscribeOn(Schedulers.elastic())
+                //.subscribeOn(Schedulers.elastic())
                 .onErrorResume(TrackerExceptions.communicationErrors, error -> Mono.empty())
                 .map(connectResponse -> new TrackerConnection(connectResponse));
     }
 
     public ConnectableFlux<TrackerConnection> connectToTrackersFlux() {
         return Flux.fromIterable(this.torrentInfo.getTrackerList())
+                .doOnNext(System.out::println)
                 .flatMap(tracker -> connectToTrackerMono(tracker))
                 .publish();
     }

### 2018-03-05 src/test/java/com/steps/MyStepdefs.java

@@ -1,15 +1,15 @@
 package com.steps;
 
-import com.utils.*;
-import cucumber.api.java.Before;
+import com.utils.PeerFakeRequestResponse;
+import com.utils.TrackerFakeRequestResponseMessage;
+import com.utils.TrackerRequestType;
+import com.utils.Utils;
 import cucumber.api.java.en.Given;
 import cucumber.api.java.en.Then;
 import main.TorrentInfo;
-import main.peer.Peer;
 import main.peer.PeersCommunicator;
 import main.peer.PeersListener;
 import main.peer.PeersProvider;
-import main.peer.peerMessages.PeerMessage;
 import main.peer.peerMessages.PieceMessage;
 import main.tracker.Tracker;
 import main.tracker.TrackerConnection;
@@ -22,32 +22,18 @@ import reactor.core.publisher.Hooks;
 import reactor.core.publisher.Mono;
 import reactor.test.StepVerifier;
 
-import java.io.IOException;
-import java.net.Socket;
 import java.util.*;
 
 import static org.mockito.Mockito.mock;
 
 public class MyStepdefs {
 
+    static {
+        Hooks.onOperatorDebug();
+    }
+
     private String torrentFilePath;
     private TorrentInfo torrentInfo = mock(TorrentInfo.class);
-
-
-    @Before
-    public void fuck() {
-        Hooks.onNextDropped(object -> {
-            if (object instanceof Socket) {
-                Socket socket = (Socket) object;
-                System.out.println("closing socket of: " + socket.getInetAddress().getHostAddress() + " " + socket.getPort());
-                try {
-                    socket.close();
-                } catch (IOException e) {
-                    e.printStackTrace();
-                }
-            }
-        });
-    }
 
     @Given("^new torrent file: \"([^\"]*)\"$")
     public void newTorrentFile(String torrentFileName) throws Throwable {
@@ -81,7 +67,7 @@ public class MyStepdefs {
         Mockito.when(this.torrentInfo.getTrackerList()).thenReturn(trackers);
     }
 
-    @Given("^additional invalid url of a tracker$")
+    @Given("^only one invalid url of a tracker$")
     public void additionalInvalidUrlOfATrackerOf() throws Throwable {
         TorrentInfo torrentInfo = Utils.readTorrentFile(this.torrentFilePath);
         String torrentHashInfo = torrentInfo.getTorrentInfoHash();
@@ -119,37 +105,47 @@ public class MyStepdefs {
                     " (we are not using it in the tests but " +
[…]
